### 2019-02-21 paper/ms.tex
halo paper init

%%
%% Beginning of file 'sample62.tex'
%%
%% Modified 2018 January
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.2 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[modern]{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
% added by DH
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\Dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\dnu}{\mbox{$\delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log g$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
\newcommand{\hipparcos}{\textit{Hipparcos}\xspace}
\newcommand{\gaia}{\textit{Gaia}\xspace}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\kepler{\emph{Kepler}\,}
\newcommand\ktwo{\emph{K2}\,}

\definecolor{linkcolor}{rgb}{0.1216,0.4667,0.7059}

\usepackage{xcolor, fontawesome}
\definecolor{twitterblue}{RGB}{64,153,255}
\newcommand\twitter[1]{\href{https://twitter.com/#1 }{\textcolor{twitterblue}{\faTwitter}\,\tt \textcolor{twitterblue}{@#1}}}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figures/}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{January 1, 2019}
\revised{January 7, 2019}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{The K2 Halo Campaign}
\shortauthors{B. J. S. Pope et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{The K2 Halo Photometry Campaign}

\correspondingauthor{Benjamin J. S. Pope \twitter{fringetracker}}
\email{benjamin.pope@nyu}

\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{NASA Sagan Fellow}

\author[0000-0002-6980-3392]{Timothy R. White}
\affiliation{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia}

\author{Daniel Huber}
\affiliation{Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

\author{Timothy R. Bedding}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

\author[0000-0003-1822-7126]{Conny Aerts}
\affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}
\affiliation{Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, NL-6500 GL Nijmegen, The Netherlands}

\author[0000-0001-9879-9313]{Tabetha Boyajian}
\affiliation{Department of Physics and Astronomy, Louisiana State University, 202 Nicholsom Hall, Baton Rouge, LA 70803, USA}

\author[0000-0003-1853-6631]{Orlagh L. Creevey}
\affiliation{Universit\'{e} C\^{o}te d'Azur, Observatoire de la C\^{o}te d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}

\author{friends}
%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.2 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
K2 bright stars. \href{https://github.com/benjaminpope/aselli}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
% \keywords{editorials, notices --- 
% miscellaneous --- catalogs --- surveys}

\section{Introduction} 
\label{sec:intro}

\section{Halo Photometry}
\label{sec:k2}

\section{Discussion}
\label{sec:discussion}

\section{Conclusions}
\label{sec:conclusions}

\section*{Acknowledgements} % add your acknowledgements text here!

We would like to thank Will Farr for his very helpful comments on the halo method.

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118).

BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples. We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands.
%

This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}. Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

\bibliography{ms}

%% This command is needed to show the entire author+affilation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample62.tex'.

### 2019-02-27 paper/ms.tex
table inits
abstract

@@
 \newcommand\twitter[1]{\href{https://twitter.com/#1 }{\textcolor{twitterblue}{\faTwitter}\,\tt \textcolor{twitterblue}{@#1}}}
+% \usepackage{ccaption}
+% \usepackage{graphicx}	% Including figure files
+% \usepackage{amsmath}	% Advanced maths commands
+% \usepackage{amssymb}	% Extra maths symbols
 
@@
 \begin{abstract}
-K2 bright stars. \href{https://github.com/benjaminpope/aselli}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!
+While the \kepler\ mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars which saturate the detector are nevertheless some of the most interesting because of the ease with which they can be observed by other instruments and the wealth of knowledge about them that is already available.
+By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign 6 onwards.
+This halo campaign reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
+Here we describe our pipeline, and present a catalogue of the halo sources, with classifications and parametrizations of their variability and remarks on interesting objects.
+These light curves are publicly available as a High Level Science Product.
+\href{https://github.com/benjaminpope/aselli}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!
 
@@
 \label{sec:k2}
+
+\section{Sample}
+\label{sec:sample}
 
@@
 
+\newpage
+% \section*{Sample}
+
+\input{all_stars_1}
+\input{all_stars_2}
+\input{all_stars_3}
+\input{all_stars_4}
+\input{all_stars_5}
 %% This command is needed to show the entire author+affilation list when

### 2019-03-01 scripts/correct_halo.py
script to correct halo data

@@ -1,0 +1,160 @@
+import numpy as np
+import matplotlib 
+import matplotlib as mpl
+
+import lightkurve 
+from lightkurve import KeplerLightCurve, KeplerTargetPixelFile
+from k2sc.standalone import k2sc_lc
+import k2sc
+
+import halophot
+from halophot.halo_tools import translate_greek
+
+from astropy.table import Table
+from astropy.io import fits
+
+import fitsio
+
+from argparse import ArgumentParser
+
+import matplotlib as mpl
+
+mpl.style.use('seaborn-colorblind')
+
+#To make sure we have always the same matplotlib settings
+#(the ones in comments are the ipython notebook settings)
+
+mpl.rcParams['figure.figsize']=(8.0,6.0)    #(6.0,4.0)
+mpl.rcParams['font.size']=18               #10 
+mpl.rcParams['savefig.dpi']= 200             #72 
+mpl.rcParams['axes.labelsize'] = 16
+mpl.rcParams['axes.labelsize'] = 16
+mpl.rcParams['xtick.labelsize'] = 12
+mpl.rcParams['ytick.labelsize'] = 12
+
+
+'''-----------------------------------------------------------------
+correct_halo.py
+
+This executable Python script allows you to detrend any single object 
+made using halophot with k2sc
+
+-----------------------------------------------------------------'''
+
+def match_cadences(halocads,lccads):
+    indices =np.array([1 if j in lccads else 0 for j in halocads])
+    return np.where(indices==1)[0]
+
+def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
+    min_p,max_p=1./24.,20.
+
+    PW,PH = 8.27, 11.69
+    
+    frequency, power, spower = get_pgram(lc.time,lc.corr_flux-lc.tr_time,min_p=min_p,max_p=max_p)
+    
+    rc('axes', labelsize=7, titlesize=8)
+    rc('font', size=6)
+    rc('xtick', labelsize=7)
+    rc('ytick', labelsize=7)
+    rc('lines', linewidth=1)
+    fig = plt.figure(figsize=(PW,PH))
+    gs1 = GridSpec(3,2)
+    gs1.update(top=0.95, bottom = 2/3.*1.05,hspace=0.0,left=0.09,right=0.96)
+    gs2 = GridSpec(1,2)
[…]

### 2019-03-05 scripts/correct_halo.py
bug fixes

@@ -1,14 +1,23 @@
 import numpy as np
+import matplotlib.pyplot as plt
+
 import matplotlib 
 import matplotlib as mpl
+from matplotlib import rc
+from matplotlib.gridspec import GridSpec
+from matplotlib.pyplot import figure, subplots, subplot
+from mpl_toolkits.axes_grid1 import make_axes_locatable, axes_size
 
 import lightkurve 
 from lightkurve import KeplerLightCurve, KeplerTargetPixelFile
 from k2sc.standalone import k2sc_lc
 import k2sc
 
+import warnings ## eeek!
+warnings.filterwarnings("ignore")
+
 import halophot
-from halophot.halo_tools import translate_greek
+from halophot.halo_tools import *
 
 from astropy.table import Table
 from astropy.io import fits
@@ -16,8 +25,6 @@ from astropy.io import fits
 import fitsio
 
 from argparse import ArgumentParser
-
-import matplotlib as mpl
 
 mpl.style.use('seaborn-colorblind')
 
@@ -136,6 +143,8 @@ if __name__ == '__main__':
     lc.flux = f[1]['corr_flux'][inds_flux]
 
     # now the magic happens
+
+    lc.campaign = int(campaign)
     lc.__class__ = k2sc_lc
     lc.k2sc()
 

### 2019-03-06 scripts/correct_halo.py
matching

@@ -122,7 +122,7 @@ if __name__ == '__main__':
 
     # read in our halo work
     all_stars = Table.read('../data/haloC%d.csv' % campaign,format='ascii')
-    star = all_stars[all_stars['Name']==starname]
+    star = all_stars[all_stars['Name']==starname.replace('_',' ')]
     epic = star['EPIC ID'].data.data[0]
 
     #load a lightkurve object with all the desired metadata

### 2019-03-06 scripts/correct_halo.py
do plots

@@ -166,4 +166,4 @@ if __name__ == '__main__':
     hdul.writeto('hlsp_halo_k2_llc_%s_-c%d.fits' % (epic,campaign),overwrite=True)
 
     if args.do_plot:
-        plot_k2sc(lc,np.nanmean(tpf.flux,axis=0),f[0][:,:].T,formal_name=translate_greek(args.name).replace('_',' ')+' Detrended')
+        plot_k2sc(lc,np.nanmean(tpf.flux,axis=0),f[0][:,:].T,formal_name=translate_greek(args.name).replace('_',' ')+' Detrended',save_file='%s_halo_k2sc.png' % args.name)

### 2019-03-06 scripts/correct_halo.py
script

@@ -163,7 +163,7 @@ if __name__ == '__main__':
     tab = fits.BinTableHDU.from_columns(cols)
 
     hdul = fits.HDUList([hdu, tab])
-    hdul.writeto('hlsp_halo_k2_llc_%s_-c%d.fits' % (epic,campaign),overwrite=True)
+    hdul.writeto('../release/hlsp_halo_k2_llc_%s_-c%d.fits' % (epic,campaign),overwrite=True)
 
     if args.do_plot:
-        plot_k2sc(lc,np.nanmean(tpf.flux,axis=0),f[0][:,:].T,formal_name=translate_greek(args.name).replace('_',' ')+' Detrended',save_file='%s_halo_k2sc.png' % args.name)
+        plot_k2sc(lc,np.nanmean(tpf.flux,axis=0),f[0][:,:].T,formal_name=translate_greek(args.name).replace('_',' ')+' Detrended',save_file='../release/%s_halo_k2sc.png' % args.name)

### 2019-03-07 paper/ms.tex
orcid for bedding
tables and paper reorganized

@@
 
-\author{Timothy R. Bedding}
+\author[0000-0001-5222-4661]{Timothy R. Bedding}
 \affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
@@
 These light curves are publicly available as a High Level Science Product.
-\href{https://github.com/benjaminpope/aselli}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!
+\href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!
 
@@
 
-This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.
+This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{scipy}; \texttt{lightkurve} \citep{lightkurve}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.
 Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
@@
 \input{all_stars_5}
+\input{all_stars_6}
+
 %% This command is needed to show the entire author+affilation list when

### 2019-03-11 paper/ms.tex
campaign 4 listed now
credits

@@
 \correspondingauthor{Benjamin J. S. Pope \twitter{fringetracker}}
-\email{benjamin.pope@nyu}
+\email{benjamin.pope@nyu.edu}
 
@@
 
-\author{Daniel Huber}
+\author[0000-0001-8832-4488 ]{Daniel Huber}
 \affiliation{Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
@@
 
+% intro kepler
+
+% briefly intro the halo method and halo literature
+
+% describe contents of paper: code, catalog, categorization, conclusions
+
 \section{Halo Photometry}
 \label{sec:k2}
+
+% describe saturation, smear
+
+% describe TV-min algorithm
+
+% describe changes with respect to Pleiades and Aldebaran papers: deathstar
+
+% incorporation of k2sc
+
+% figure
 
@@
 
+% link to tables 
+% normal apertures in 6
+
+The full sample of stars for which halo apertures were obtained is listed in Tables~\ref{table_0}--\ref{table_5}, broken down by Campaign.
+While some very bright stars were observed with conventional apertures as part of these programs, simple aperture photometry is satisfactory on these targets and we exclude them from the present discussion and data release, which is oriented strictly towards targets only observable with halo photometry.
+We make an exception for Spica, which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture.
+In Campaign~6 it was assigned a normal aperture by mistake and simple aperture photometry performed extremely poorly, so we have processed it with the halo pipeline.
+
+% short cadence availability
+
+% breakdown of main sequence vs giants
+
+% note interesting targets: Aldebaran; Spica; Hyades; rho Leo
+
+Some of the objects here have been previously published, but we here provide the first public data releases for the Pleiades' Seven Sisters \citep{White2017}, Aldebaran \citep{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{arentoft2019}.
+
 \section{Discussion}
@@
 
+% how well did we do?
+
 \section{Conclusions}
 \label{sec:conclusions}
+
+% pretty good sample
+
+% do hot star asteroseismology and red giants as benchmarks, interferometry
+Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.) and the Hyades giants (White et al., in prep.).
+In addition to this, we aim to separately publish asteroseismic catalogues of the red giants (Yu et al., in prep.) and main-sequence stars (Greklek-McKeon et al., in prep.).
+
+% do k2 smear after that
+
+% tess halo
 
@@
 TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118).
+The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a DDT program in Campaign 4 as GO4901.
+We are grateful for the associated funding provided by the K2 GO office which has been essential in bringing this project to fruition.
 

### 2019-03-11 paper/ms.tex
comments and short cadence and stuff

@@
 % short cadence availability 
+Seven stars in Campaign~13 and one in Campaign~16 were not only assigned long-cadence halo apertures, but also downloaded at short cadence.
+TV-min halo photometry appears to perform poorly on short-cadence data, however, and we do not consider the data products for these stars to be satisfactory for an initial data release.
+This may be to do with the total variation being a poor proxy for noise in the light curves, with relatively fewer thruster-firing jumps and relatively higher white noise.
+The long-cadence data appear to be of normal quality.
 
@@
 
-Some of the objects here have been previously published, but we here provide the first public data releases for the Pleiades' Seven Sisters \citep{White2017}, Aldebaran \citep{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{arentoft2019}.
+Some of the objects here have been previously published, but we here provide the first public data releases for the Pleiades' Seven Sisters \citep{White2017}, Aldebaran \citep{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{Arentoft2019}, as well as $\rho$~Leo with halo photometry but without using the TV-min method \citep{Aerts2018}.
 
@@
 % do k2 smear after that
+The sample of K2 bright stars presented here only includes those with halo apertures, but while some others are available conventionally, many were not assigned target pixels and were not downloaded at all.
+Light curves for many of these stars can nevertheless be obtained with smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
+These can be used to recover the 102 brightest otherwise-unobserved stars in nominal \kepler (Pope et al., in prep.), and also in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more difficult.
+A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.
 

### 2019-03-12 paper/ms.tex
gadigal
additions

@@
 Here we describe our pipeline, and present a catalogue of the halo sources, with classifications and parametrizations of their variability and remarks on interesting objects.
-These light curves are publicly available as a High Level Science Product.
+These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST).
 \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!
@@
 
-% describe saturation, smear
+% describe saturation
 
 % describe TV-min algorithm
+We use the method of halo photometry, first described by \citet{White2017} and with further developments by \citet{Farr2018}.
+
+% smear
+This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
+While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.
 
@@
 % incorporation of k2sc
+While the TV-min procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion.
+In order to correct these, we employ the \texttt{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \texttt{POS\_CORR}) in pixels $(x,y)$.
+The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction in space evaluated for fixed time represents the pointing systematics and is subtracted from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
 
@@
 This may be to do with the total variation being a poor proxy for noise in the light curves, with relatively fewer thruster-firing jumps and relatively higher white noise.
-The long-cadence data appear to be of normal quality.
+The long-cadence data for these stars appear to be of normal quality.
 
@@
 The sample of K2 bright stars presented here only includes those with halo apertures, but while some others are available conventionally, many were not assigned target pixels and were not downloaded at all.
-Light curves for many of these stars can nevertheless be obtained with smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
-These can be used to recover the 102 brightest otherwise-unobserved stars in nominal \kepler (Pope et al., in prep.), and also in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more difficult.
+Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., in prep.), and this can also be done in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more difficult.
 A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.
@@
 % tess halo 
+The halo method naturally extends to other contexts where simple aperture photometry is not possible, such as for saturated stars observed by the Transiting Exoplanet Survey Satellite \citep[TESS;][]{tess}.
+Although the saturation limit is brighter ($T_{mag} \sim 6$) and this problem accordingly affects fewer stars and less badly, there are situations such as for $\alpha$~Centauri or $\beta$~Hydri where the bleed column reaches the edge of the chip and a SAP light curve is irrecoverable.
+We expect that TV-min halo photometry will therefore be valuable in ensuring that TESS can observe even the very brightest stars.
 
@@
 We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands.
+We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and to their elders past, present, and future.
 %

### 2019-03-12 paper/ms.tex
equations

@@
 These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST).
-\href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!
-
+\href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % git link shamelessly borrowed from Luger!
 \end{abstract}
@@
 We use the method of halo photometry, first described by \citet{White2017} and with further developments by \citet{Farr2018}.
+Because SAP is not possible, we consider instead the unsaturated pixels $p_j$ at the wings of the broad and complex PSF, and construct a light curve as a linear combination with weights $w_j$ of these time series, so that flux at cadence $i$ is
+
+\begin{equation}
+    f_i \equiv \sum_j {w_j p_{ij}}.
+\end{equation}
+
+\noindent The weights are chosen to minimize the Total Variation
+
+\begin{equation}
+    TV \equiv \frac{\sum_i{|f_i - f_{i-1}|}}{\sum_i {f_i}},
+\end{equation}
+
+\noindent which can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
 
@@
 % how well did we do?
+
+% interesting EB
+
+% RGs, Classical pulsators
 

### 2019-03-13 scripts/correct_halo.py
edits to scripts

@@ -94,7 +94,11 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     ax_weightmap.set_title('TV-Min Weight Map')
 
     if save_file is not None:
-        plt.savefig(save_file)
+        try:
+            for fname in save_file:
+                plt.savefig(fname)
+        except:
+            plt.savefig(save_file)
 '''-----------------------------------------------------------------
 
 An example call is 
@@ -166,4 +170,4 @@ if __name__ == '__main__':
     hdul.writeto('../release/hlsp_halo_k2_llc_%s_-c%d.fits' % (epic,campaign),overwrite=True)
 
     if args.do_plot:
-        plot_k2sc(lc,np.nanmean(tpf.flux,axis=0),f[0][:,:].T,formal_name=translate_greek(args.name).replace('_',' ')+' Detrended',save_file='../release/%s_halo_k2sc.png' % args.name)
+        plot_k2sc(lc,np.nanmean(tpf.flux,axis=0),f[0][:,:].T,formal_name=translate_greek(args.name).replace('_',' ')+' Detrended',save_file=['../release/%s_halo_k2sc.png' % args.name,'../release/%s_halo_k2sc.pdf' % args.name])

### 2019-03-20 paper/ms.tex
autograd citation
introduction

@@
 % intro kepler
+The \kepler Space Telescope was launched with a goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}.
+In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler the exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and these saturated stars were intentionally avoided.
+In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars.
+While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry or high-resolution spectroscopy, and they typically have long histories of previous observations.
 
 % briefly intro the halo method and halo literature
+In order to recover precise photometry of the brightest stars in \ktwo, we have developed two main approaches, `smear' and `halo' photometry.
+Smear photometry \citep{Pope2016} uses collateral calibration data to recover light curves of stars which were not necessarily conventionally targeted.
+The more precise method of halo photometry, which is the subject of this paper, uses the broad `halo' of scattered light around a saturated star to recover relative photometry, by constructing a light curve as a linear combination of individual pixel time series and minimizing a Total Variation objective function (TV-min).
+It has been employed for example on the Pleiades \citep{White2017} and the brightest-ever star on \kepler silicon, Aldebaran \citep{Farr2018}, recovering photometry with a precision nearly that of normally-obtained \ktwo observations of unsaturated stars.
+Unlike smear, this requires downloading data out to a 12--20~pixel radius around each star, and has accordingly only been possible for stars that were specifically targeted with apertures optimized for this method and for a small number of other stars for which this is fortuitously the case.
 
 % describe contents of paper: code, catalog, categorization, conclusions
+In this Paper we describe the complete catalog of long-cadence \ktwo halo light curves which we have made publicly available.
+We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability.
+We also document the main changes in the halo data reduction pipeline, \texttt{halophot}, with respect to previous releases.
+These include oscillating red giants, pulsating and quiet main sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with space photometry.
+We hope that this diverse catalog of light curves will be useful for an equally-diverse range of astrophysical investigations.
 
@@
 \noindent which can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
-
+TV is a convex objective function and has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
 % smear

### 2019-03-21 paper/ms.tex
change the output format

@@
 % intro kepler
-The \kepler Space Telescope was launched with a goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}.
+The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}.
 In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler the exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and these saturated stars were intentionally avoided.
@@
 In Campaign~6 it was assigned a normal aperture by mistake and simple aperture photometry performed extremely poorly, so we have processed it with the halo pipeline.
+The stars in Campaign~18 were also on-silicon in Campaign~5, but were not assigned apertures suitable for halo photometry in C5.
+A possible further extension of the present work would be to recover C5 light curves for these objects using either or both of smear or modified halo photometry.
 
@@
 TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118).
-The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a DDT program in Campaign 4 as GO4901.
+The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a Director's Discretionary Time program in Campaign 4 as GO4901.
 We are grateful for the associated funding provided by the K2 GO office which has been essential in bringing this project to fruition.

### 2019-03-21 scripts/correct_halo.py

@@ -113,6 +113,8 @@ if __name__ == '__main__':
         help='Campaign number')
     ap.add_argument('--do-plot', action = 'store_true', default = True, \
                     help = 'produce plots')
+    ap.add_argument('--just-plot', action = 'store_true', default = False, \
+                    help = 'only produce plots')
 
     args = ap.parse_args()
 
@@ -120,7 +122,6 @@ if __name__ == '__main__':
     ddir = '../reduced/c%d/' % campaign
     starname = args.name
     fname = ddir+'%s_halo_lc_o1.fits' % starname
-
     f = fitsio.FITS(fname)
     hdr = fitsio.read_header(fname)
 
@@ -132,6 +133,7 @@ if __name__ == '__main__':
     #load a lightkurve object with all the desired metadata
     tpf = lightkurve.open('../data/ktwo%d-c%02d_lpd-targ.fits.gz' % (epic,campaign))
     lc = tpf.to_lightcurve('aperture')
+
     lc.pos_corr1 = tpf.pos_corr1
     lc.pos_corr2 = tpf.pos_corr2
     lc.primary_header = tpf.hdu[0].header
@@ -150,24 +152,39 @@ if __name__ == '__main__':
 
     lc.campaign = int(campaign)
     lc.__class__ = k2sc_lc
-    lc.k2sc()
 
-    # save data
-    to_save = ['time', 'flux', 'flux_err','centroid_col', 'centroid_row', 'quality', 'cadenceno','pos_corr1', 'pos_corr2','tr_position', 'tr_time','corr_flux']
+    if not args.just_plot:
+        lc.k2sc()
 
-    dummy = fits.getheader('../data/ktwo%d-c%02d_lpd-targ.fits.gz' % (epic,campaign)) # get the old header from the TPF
-    dummy['NAXIS']=1
-    dummy['halo'] =(halophot.__version__,'halophot version')
-    dummy['order']=(1,'halophot TV order')
-    dummy['sub']=(1,'halophot subsampling')
-    dummy['starname']=(starname,'Star Identifier')
+        # save data
+        to_save = ['time', 'flux', 'flux_err','centroid_col', 'centroid_row', 'quality', 'cadenceno','pos_corr1', 'pos_corr2','tr_position', 'tr_time','corr_flux']
 
[…]

### 2019-03-21 scripts/correct_halo.py
campaign name fubar

@@ -126,7 +126,11 @@ if __name__ == '__main__':
     hdr = fitsio.read_header(fname)
 
     # read in our halo work
-    all_stars = Table.read('../data/haloC%d.csv' % campaign,format='ascii')
+    if campaign in [91,92, 101, 102, 111,112]:
+        campaign_name = int(str(campaign)[:-1])
+    else:
+        campaign_name = campaign
+    all_stars = Table.read('../data/haloC%d.csv' % campaign_name,format='ascii')
     star = all_stars[all_stars['Name']==starname.replace('_',' ')]
     epic = star['EPIC ID'].data.data[0]
 
@@ -171,18 +175,18 @@ if __name__ == '__main__':
         tab = fits.BinTableHDU.from_columns(cols)
 
         hdul = fits.HDUList([hdu, tab])
-        hdul.writeto('../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.fits' % (campaign,epic,campaign),overwrite=True)
+        hdul.writeto('../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.fits' % (campaign_name,epic,campaign),overwrite=True)
 
     else:
         args.do_plot = True # in case you forgot!  
-        data = Table.read('../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.fits' % (campaign,epic,campaign))
+        data = Table.read('../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.fits' % (campaign_name,epic,campaign))
         lc.corr_flux = data['corr_flux']
         lc.tr_position = data['tr_position']
         lc.tr_time = data['tr_time']
 
     if args.do_plot:
         plot_k2sc(lc,np.nanmean(tpf.flux,axis=0),f[0][:,:].T,formal_name=translate_greek(args.name).replace('_',' ')+'(EPIC %s) Detrended' % epic,
-            save_file=['../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.png' % (campaign,epic,campaign),'../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.png' % (campaign,epic,campaign)])
[…]

### 2019-03-21 scripts/correct_halo.py
space

@@ -126,7 +126,7 @@ if __name__ == '__main__':
     hdr = fitsio.read_header(fname)
 
     # read in our halo work
-    if campaign in [91,92, 101, 102, 111,112]:
+    if campaign in [91,92, 101, 102, 111, 112]:
         campaign_name = int(str(campaign)[:-1])
     else:
         campaign_name = campaign
@@ -185,8 +185,8 @@ if __name__ == '__main__':
         lc.tr_time = data['tr_time']
 
     if args.do_plot:
-        plot_k2sc(lc,np.nanmean(tpf.flux,axis=0),f[0][:,:].T,formal_name=translate_greek(args.name).replace('_',' ')+'(EPIC %s) Detrended' % epic,
-            save_file=['../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.png' % (campaign_name,epic,campaign),'../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.png' % (campaign,epic,campaign)])
+        plot_k2sc(lc,np.nanmean(tpf.flux,axis=0),f[0][:,:].T,formal_name=translate_greek(args.name).replace('_',' ')+' (EPIC %s) Detrended' % epic,
+            save_file=['../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.png' % (campaign_name,epic,campaign),'../release/c%d/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.pdf' % (campaign,epic,campaign)])
 
 
 

### 2019-03-27 paper/ms.tex
some updates

@@
 %% using aastex version 6.2
-\documentclass[modern]{aastex62}
+\documentclass[twocolumn]{aastex62}
 
@@
 \author[0000-0001-8832-4488 ]{Daniel Huber}
-\affiliation{Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
+\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
 \affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
@@
 While the TV-min procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion.
-In order to correct these, we employ the \texttt{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \texttt{POS\_CORR}) in pixels $(x,y)$.
+In order to correct these, we employ the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$.
 The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction in space evaluated for fixed time represents the pointing systematics and is subtracted from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
+The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112.
+As a result \textsc{k2sc}-corrected data are not available for these targets.
 

### 2019-03-27 scripts/correct_halo.py

@@ -111,31 +111,56 @@ if __name__ == '__main__':
     ap.add_argument('-name', default='test',type=str,help='Target name')
     ap.add_argument('-c', '--campaign', metavar='C',default=13, type=int, 
         help='Campaign number')
+    ap.add_argument('--ddir',default=None,type=str,help='Data directory')
+    ap.add_argument('--savedir',default=None,type=str,help='output directory')
     ap.add_argument('--do-plot', action = 'store_true', default = True, \
                     help = 'produce plots')
     ap.add_argument('--just-plot', action = 'store_true', default = False, \
                     help = 'only produce plots')
+    ap.add_argument('--epic',default=200000000,type=str,help='EPIC Number')
+    ap.add_argument('--tpf-fname',default=None,type=str,help='TPF Filename')
 
     args = ap.parse_args()
 
     campaign = args.campaign
-    ddir = '../reduced/c%d/' % campaign
-    starname = args.name
-    fname = ddir+'%s_halo_lc_o1.fits' % starname
-    f = fitsio.FITS(fname)
-    hdr = fitsio.read_header(fname)
 
-    # read in our halo work
     if campaign in [91,92, 101, 102, 111, 112]:
         campaign_name = int(str(campaign)[:-1])
     else:
         campaign_name = campaign
-    all_stars = Table.read('../data/haloC%d.csv' % campaign_name,format='ascii')
-    star = all_stars[all_stars['Name']==starname.replace('_',' ')]
-    epic = star['EPIC ID'].data.data[0]
+
+    if args.ddir is not None:
+        ddir = args.ddir
+    else:
+        ddir = '../reduced/c%d/' % campaign_name
+
+    if args.savedir is not None:
+        savedir = args.savedir
+    else:
+        savedir='../release/c%d' % campaign_name
+
+    starname = args.name
+    fname = '%s/%s_halo_lc_o1.fits' % (ddir,starname)
+    f = fitsio.FITS(fname)
+    hdr = fitsio.read_header(fname)
+
+    # read in our halo work
+
 
     #load a lightkurve object with all the desired metadata
[…]

### 2019-03-27 scripts/correct_halo.py
names

@@ -82,7 +82,7 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
 
     plot_lc(ax_lctime,lc.time,lc.flux-lc.tr_time+np.nanmedian(lc.tr_time),formal_name,trend=lc.tr_position)
     plot_lc(ax_lcpos,lc.time,lc.flux-lc.tr_position+np.nanmedian(lc.tr_position),formal_name,trend=lc.tr_time)
-    plot_lc(ax_lcwhite,lc.time,lc.corr_flux-lc.tr_time,formal_name+': Whitened')
+    plot_lc(ax_lcwhite,lc.time,(lc.corr_flux-lc.tr_time)+np.nanmedian(lc.tr_time),formal_name+': Whitened')
     plot_weightmap(ax_weightmap,weightmap,formal_name)
     plot_fluxmap(ax_fluxmap,image,formal_name)
     plot_pgram(ax_periodogram,frequency,power,spower,formal_name)        
@@ -111,8 +111,9 @@ if __name__ == '__main__':
     ap.add_argument('-name', default='test',type=str,help='Target name')
     ap.add_argument('-c', '--campaign', metavar='C',default=13, type=int, 
         help='Campaign number')
-    ap.add_argument('--ddir',default=None,type=str,help='Data directory')
-    ap.add_argument('--savedir',default=None,type=str,help='output directory')
+    ap.add_argument('--ddir-raw',default=None,type=str,help='Raw data directory')
+    ap.add_argument('--ddir-halo',default=None,type=str,help='Halo data directory')
+    ap.add_argument('--savedir',default=None,type=str,help='Output directory')
     ap.add_argument('--do-plot', action = 'store_true', default = True, \
                     help = 'produce plots')
     ap.add_argument('--just-plot', action = 'store_true', default = False, \
@@ -129,10 +130,15 @@ if __name__ == '__main__':
     else:
         campaign_name = campaign
 
-    if args.ddir is not None:
-        ddir = args.ddir
+    if args.ddir_halo is not None:
+        ddir_halo = args.ddir_halo
     else:
-        ddir = '../reduced/c%d/' % campaign_name
+        ddir_halo = '../reduced/c%d/' % campaign_name
+
+    if args.ddir_raw is not None:
+        ddir_raw = args.ddir_raw
+    else:
+        ddir_raw = '../data/' 
 
[…]

### 2019-03-28 scripts/correct_halo.py
objective function needs to change

@@ -120,6 +120,7 @@ if __name__ == '__main__':
                     help = 'only produce plots')
     ap.add_argument('--epic',default=200000000,type=str,help='EPIC Number')
     ap.add_argument('--tpf-fname',default=None,type=str,help='TPF Filename')
+    ap.add_argument('--objective', default='tv',type=str,help='Objective function: can be tv, tv_o2, l2v, or l3v')
 
     args = ap.parse_args()
 
@@ -145,8 +146,10 @@ if __name__ == '__main__':
     else:
         savedir='../release/c%d' % campaign_name
 
+    objective = args.objective
+
     starname = args.name
-    fname = '%s/%s_halo_lc_o1.fits' % (ddir_halo,starname)
+    fname = '%s/%s_halo_lc_%s.fits' % (ddir_halo,starname,objective)
     f = fitsio.FITS(fname)
     hdr = fitsio.read_header(fname)
 
@@ -198,7 +201,7 @@ if __name__ == '__main__':
         dummy = fits.getheader('%s/%s' % (ddir_raw,tpf_fname)) # get the old header from the TPF
         dummy['NAXIS']=1
         dummy['halo'] =(halophot.__version__,'halophot version')
-        dummy['order']=(1,'halophot TV order')
+        dummy['objective']=(objective,'halophot objective')
         dummy['sub']=(1,'halophot subsampling')
         dummy['starname']=(starname,'Star Identifier')
 

### 2019-03-28 data/download_sc.sh
download short cadence

@@ -1,0 +1,19 @@
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c91/200000000/71000/ktwo200071159-c91_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c92/200000000/71000/ktwo200071159-c92_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c111/200100000/29000/ktwo200129034-c111_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c111/200100000/29000/ktwo200129035-c111_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c112/200100000/47000/ktwo200147464-c112_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c112/200100000/47000/ktwo200147465-c112_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c13/200100000/73000/ktwo200173877-c13_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c13/200100000/73000/ktwo200173878-c13_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c13/200100000/73000/ktwo200173879-c13_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c13/200100000/73000/ktwo200173880-c13_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c13/200100000/73000/ktwo200173881-c13_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c13/200100000/73000/ktwo200173882-c13_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c13/200100000/73000/ktwo200173883-c13_spd-targ.fits.gz
+wget -q http://archive.stsci.edu/missions/k2/target_pixel_files/c13/200100000/73000/ktwo200173884-c13_spd-targ.fits.gz
[…]

### 2019-03-29 paper/ms.tex
paper updates

@@
 
-\author[0000-0001-8832-4488 ]{Daniel Huber}
-\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
-\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
-\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+\author[0000-0003-1822-7126]{Conny Aerts}
+\affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}
+\affiliation{Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, NL-6500 GL Nijmegen, The Netherlands}
+
+\author[0000-0003-1453-0574]{Suzanne Aigrain}
+\affiliation{Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK}
 
@@
 \affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
-
-\author[0000-0003-1822-7126]{Conny Aerts}
-\affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}
-\affiliation{Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, NL-6500 GL Nijmegen, The Netherlands}
-
 \author[0000-0001-9879-9313]{Tabetha Boyajian}
@@
 \affiliation{Universit\'{e} C\^{o}te d'Azur, Observatoire de la C\^{o}te d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}
+
+\author[0000-0001-8832-4488 ]{Daniel Huber}
+\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
+\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
 
@@
 
-\noindent The weights are chosen to minimize the Total Variation
+\noindent The weights are chosen to minimize the a modified Total Variation
 
 \begin{equation}
-    TV \equiv \frac{\sum_i{|f_i - f_{i-1}|}}{\sum_i {f_i}},
+    TV \equiv \frac{\sum_i{|f_i - f_{i-l}|}}{\sum_i {f_i}},
 \end{equation}
 
-\noindent which can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
+\noindent which for $l = 1$ is the standard Total Variation and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
+We introduce a lag parameter $l$ in order to allow for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.
 TV is a convex objective function and has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
@@
 % describe changes with respect to Pleiades and Aldebaran papers: deathstar
+
+% benchmarking with lags and
 

### 2019-04-01 paper/ms.tex
typo
tess ninja 2 acknowledgement
figure included

@@
 
-\noindent The weights are chosen to minimize the a modified Total Variation
+\noindent The weights are chosen to minimize the modified Total Variation
 
@@
 
+\begin{figure*}
+\plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.png}
+\end{figure*}
+
 \section{Conclusions}
@@
 We are grateful for the associated funding provided by the K2 GO office which has been essential in bringing this project to fruition.
+
+This project was developed in part at the Building Early Science with TESS meeting, which took place in March 2019 at the University of Chicago.
 

### 2019-04-01 paper/ms.tex
modern format
updates

@@
 %% using aastex version 6.2
-\documentclass[twocolumn]{aastex62}
+\documentclass[modern]{aastex62}
 
@@
 
-% describe TV-min algorithm
-We use the method of halo photometry, first described by \citet{White2017} and with further developments by \citet{Farr2018}.
+% describe halo algorithm
+We use an extension of the method of halo photometry, first described by \citet{White2017} and with further developments by \citet{Farr2018}.
 Because SAP is not possible, we consider instead the unsaturated pixels $p_j$ at the wings of the broad and complex PSF, and construct a light curve as a linear combination with weights $w_j$ of these time series, so that flux at cadence $i$ is
@@
 
-\noindent The weights are chosen to minimize the modified Total Variation
+\noindent The weights are chosen to minimize an objective function
 
 \begin{equation}
-    TV \equiv \frac{\sum_i{|f_i - f_{i-l}|}}{\sum_i {f_i}},
+    \Lambda_{k,l} \equiv \frac{\sum_i{|f_i - f_{i-l}|^k}}{\sum_i {f_i}},
 \end{equation}
 
-\noindent which for $l = 1$ is the standard Total Variation and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
-We introduce a lag parameter $l$ in order to allow for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.
-TV is a convex objective function and has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
+\noindent which is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$.
+For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation as used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
+The lag parameter $l$ allow for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.
+The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise.
+TV is a convex objective function \textcolor{red}{and I think the generalizations are too} and $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
+
 % smear
@@
 % incorporation of k2sc
-While the TV-min procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion.
+While the halo procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion.
 In order to correct these, we employ the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$.
@@
 Seven stars in Campaign~13 and one in Campaign~16 were not only assigned long-cadence halo apertures, but also downloaded at short cadence.
-TV-min halo photometry appears to perform poorly on short-cadence data, however, and we do not consider the data products for these stars to be satisfactory for an initial data release.
-This may be to do with the total variation being a poor proxy for noise in the light curves, with relatively fewer thruster-firing jumps and relatively higher white noise.
-The long-cadence data for these stars appear to be of normal quality.
+For these targets we have provided both long and short cadence reductions.
 

### 2019-04-03 scripts/correct_halo.py
short cadence

@@ -38,6 +38,7 @@ mpl.rcParams['axes.labelsize'] = 16
 mpl.rcParams['axes.labelsize'] = 16
 mpl.rcParams['xtick.labelsize'] = 12
 mpl.rcParams['ytick.labelsize'] = 12
+mpl.rcParams["font.family"] = "Times New Roman"
 
 
 '''-----------------------------------------------------------------

### 2019-04-03 scripts/correct_halo.py
fix

@@ -135,7 +135,7 @@ if __name__ == '__main__':
     if args.ddir_halo is not None:
         ddir_halo = args.ddir_halo
     else:
-        ddir_halo = '../reduced/c%d/' % campaign_name
+        ddir_halo = '../reduced/c%d/' % campaign
 
     if args.ddir_raw is not None:
         ddir_raw = args.ddir_raw
@@ -145,7 +145,7 @@ if __name__ == '__main__':
     if args.savedir is not None:
         savedir = args.savedir
     else:
-        savedir='../release/c%d' % campaign_name
+        savedir='../release/c%d' % campaign
 
     objective = args.objective
 

### 2019-04-03 scripts/correct_halo.py
trend display

@@ -57,8 +57,8 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     min_p,max_p=1./24.,20.
 
     PW,PH = 8.27, 11.69
-    
-    frequency, power, spower = get_pgram(lc.time,lc.corr_flux-lc.tr_time,min_p=min_p,max_p=max_p)
+    trend = savgol_filter(lc_first_try,201,2)
+    frequency, power, spower = get_pgram(lc.time,lc.corr_flux-trend+np.nanmedian(trend),min_p=min_p,max_p=max_p)
     
     rc('axes', labelsize=7, titlesize=8)
     rc('font', size=6)
@@ -81,8 +81,8 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     ax_periodogram   = subplot(gs3[0,:])
     ax_logpgram    = subplot(gs3[1,:])
 
-    plot_lc(ax_lctime,lc.time,lc.flux-lc.tr_time+np.nanmedian(lc.tr_time),formal_name,trend=lc.tr_position)
-    plot_lc(ax_lcpos,lc.time,lc.flux-lc.tr_position+np.nanmedian(lc.tr_position),formal_name,trend=lc.tr_time)
+    plot_lc(ax_lctime,lc.time,[lc.flux-lc.tr_time+np.nanmedian(lc.tr_time)],formal_name,trends=[lc.tr_position])
+    plot_lc(ax_lcpos,lc.time,lc.flux-lc.tr_position+np.nanmedian(lc.tr_position),formal_name,trends=[lc.tr_time,trend])
     plot_lc(ax_lcwhite,lc.time,(lc.corr_flux-lc.tr_time)+np.nanmedian(lc.tr_time),formal_name+': Whitened')
     plot_weightmap(ax_weightmap,weightmap,formal_name)
     plot_fluxmap(ax_fluxmap,image,formal_name)

### 2019-04-03 paper/ms.tex
paper updates

@@
 
+\begin{figure*}
+\plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.pdf}
+\end{figure*}
+
 \section{Sample}
@@
 For these targets we have provided both long and short cadence reductions.
+Following the analysis in Section~\ref{optimization} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$~cad and on choice of objective function, for consistency with  long cadence we have adopted a 300~cadence lag (i.e.
+$30 \times$ the long cadence lag of 10) and the L1 TV objective function.
+With their long timeseries the short cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo lightcurves.
 
@@
 % RGs, Classical pulsators
-
-\begin{figure*}
-\plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.png}
-\end{figure*}
 

### 2019-04-03 paper/ms.tex
figures

@@
 \plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.pdf}
+\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis.}
+\end{figure*}
+
+\begin{figure*}
+\plottwo{lag_lc_cdpp.pdf}{lag_sc.pdf}
+\caption{Behaviour of long cadence (left) and short cadence (right) CDPP as a function of lag parameter $l$.
+For long cadence this shows a minimum for L1 norm and $l=10$, i.e.
+for objective function $\Lambda_{1,10}$.
+For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1, L2 or~L3 norms.}
 \end{figure*}

### 2019-04-03 paper/ms.tex
figures
meta optimizing

@@
 
-\section{Halo Photometry}
-\label{sec:k2}
+\section{Halo Photometry Method}
+\label{method}
 
@@
 The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise.
-TV is a convex objective function \textcolor{red}{and I think the generalizations are too} and $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
+TV is a convex objective function \textcolor{red}{and I think the generalizations are too} and $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
 
@@
 
+% benchmarking with lags and objective functions
+
+In order to choose the objective function $\Lambda_{k,l}$, we have selected the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the halo sample and one with very little high frequency variability detected or predicted, which was also observed at short cadence.
+We choose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better.
+We calculate halo lightcurves and their CDPPs for $k \in \{1,2,3\}$, and $l \in [1,50]$ for long cadence and (sparsely) $l \in [1,2500]$ for short cadence data.
+The results are displayed in Figure~\ref{cdpps}.
+We find that for long cadence data, the L1 norm (TV) and a lag of 10 provide the best CDPP, which is unsurprising given that this is a slightly shorter lag than the 12~cadence thruster firing period.
+In this context we can understand the optimum as TV-min suppressing systematics on the same timescale as they occur.
+On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for all values of $k$ and improves very slowly with $l$ for longer lags.
+In calculating lightcurves here, seeing the very weak dependence of short cadence CDPP on $l$, we calculate our final light curves with TV and a lag of 300 cadences for consistency with the long cadence method.
+
+\begin{figure*}
+\plottwo{lag_lc_cdpp.pdf}{lag_sc.pdf}
+\caption{Behaviour of long cadence (left) and short cadence (right) 6.5~hour CDPP for the quiet dwarf 36~Ophiuchi as a function of lag parameter $l$.
+For long cadence this shows a minimum for L1 norm and $l=10$, i.e.
+for objective function $\Lambda_{1,10}$.
+For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1, L2 or~L3 norms.}
+\label{cdpps}
+\end{figure*}
+
 % describe changes with respect to Pleiades and Aldebaran papers: deathstar
 
-% benchmarking with lags and
+In addition to these changes in objective function, we have also added a feature `\texttt{deathstar}' to deal with contamination.
+We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out.
+\textcolor{red}{More here from Tim.}
 
@@
 \caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis.}
-\end{figure*}
-
-\begin{figure*}
-\plottwo{lag_lc_cdpp.pdf}{lag_sc.pdf}
-\caption{Behaviour of long cadence (left) and short cadence (right) CDPP as a function of lag parameter $l$.
-For long cadence this shows a minimum for L1 norm and $l=10$, i.e.
-for objective function $\Lambda_{1,10}$.
-For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1, L2 or~L3 norms.}
 \end{figure*}
@@
 For these targets we have provided both long and short cadence reductions.
-Following the analysis in Section~\ref{optimization} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$~cad and on choice of objective function, for consistency with  long cadence we have adopted a 300~cadence lag (i.e.
+Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$~cad and on choice of objective function, for consistency with  long cadence we have adopted a 300~cadence lag (i.e.
 $30 \times$ the long cadence lag of 10) and the L1 TV objective function.

### 2019-04-04 scripts/correct_halo.py
first try argh

@@ -57,7 +57,7 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     min_p,max_p=1./24.,20.
 
     PW,PH = 8.27, 11.69
-    trend = savgol_filter(lc_first_try,201,2)
+    trend = savgol_filter(lc.corr_flux,201,2)
     frequency, power, spower = get_pgram(lc.time,lc.corr_flux-trend+np.nanmedian(trend),min_p=min_p,max_p=max_p)
     
     rc('axes', labelsize=7, titlesize=8)

### 2019-04-04 scripts/correct_halo.py
first try argh

@@ -81,7 +81,7 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     ax_periodogram   = subplot(gs3[0,:])
     ax_logpgram    = subplot(gs3[1,:])
 
-    plot_lc(ax_lctime,lc.time,[lc.flux-lc.tr_time+np.nanmedian(lc.tr_time)],formal_name,trends=[lc.tr_position])
+    plot_lc(ax_lctime,lc.time,lc.flux-lc.tr_time+np.nanmedian(lc.tr_time),formal_name,trends=[lc.tr_position])
     plot_lc(ax_lcpos,lc.time,lc.flux-lc.tr_position+np.nanmedian(lc.tr_position),formal_name,trends=[lc.tr_time,trend])
     plot_lc(ax_lcwhite,lc.time,(lc.corr_flux-lc.tr_time)+np.nanmedian(lc.tr_time),formal_name+': Whitened')
     plot_weightmap(ax_weightmap,weightmap,formal_name)

### 2019-04-04 scripts/correct_halo.py
trend

@@ -57,7 +57,7 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     min_p,max_p=1./24.,20.
 
     PW,PH = 8.27, 11.69
-    trend = savgol_filter(lc.corr_flux,201,2)
+    trend = savgol_filter(lc.corr_flux,501,2)
     frequency, power, spower = get_pgram(lc.time,lc.corr_flux-trend+np.nanmedian(trend),min_p=min_p,max_p=max_p)
     
     rc('axes', labelsize=7, titlesize=8)

### 2019-04-04 scripts/correct_halo.py
polynomial instead

@@ -57,7 +57,8 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     min_p,max_p=1./24.,20.
 
     PW,PH = 8.27, 11.69
-    trend = savgol_filter(lc.corr_flux,501,2)
+    poly = np.poly1d(np.polyfit(lc.time,lc.corr_flux,15))
+    trend = poly(lc.time)
     frequency, power, spower = get_pgram(lc.time,lc.corr_flux-trend+np.nanmedian(trend),min_p=min_p,max_p=max_p)
     
     rc('axes', labelsize=7, titlesize=8)

### 2019-04-04 scripts/correct_halo.py
infinite points

@@ -57,7 +57,8 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     min_p,max_p=1./24.,20.
 
     PW,PH = 8.27, 11.69
-    poly = np.poly1d(np.polyfit(lc.time,lc.corr_flux,15))
+    m = np.isfinite(lc.corr_flux)
+    poly = np.poly1d(np.polyfit(lc.time[m],lc.corr_flux[m],15))
     trend = poly(lc.time)
     frequency, power, spower = get_pgram(lc.time,lc.corr_flux-trend+np.nanmedian(trend),min_p=min_p,max_p=max_p)
     

### 2019-04-05 paper/ms.tex
updates

@@
 % describe saturation
+The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30~min) and short (1~min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}.
+Beyond this point, additional photons cause excess electrons to `bleed' into adjacent pixels in both directions along the column containing the bright star.
+This process occurs conservatively and simple aperture photometry (SAP) adding all the flux contained in a window around the bleed column has recovered light curves with precisions close to the photon noise limit of stars as bright as 16~Cyg~AB, $\theta$~Cyg and RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}.
+In the nominal \kepler mission this was not attempted for all such bright stars, and in \ktwo, the several-pixel spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.
+While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is rendered impossible for the very brightest stars whose bleed columns may run to the edge of the detector.
+Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo.
+It was therefore necessary to develop a method to recover good light curves from a smaller number of unsaturated pixels in a compact aperture around bright stars: halo photometry.
 
 % describe halo algorithm
-We use an extension of the method of halo photometry, first described by \citet{White2017} and with further developments by \citet{Farr2018}.
-Because SAP is not possible, we consider instead the unsaturated pixels $p_j$ at the wings of the broad and complex PSF, and construct a light curve as a linear combination with weights $w_j$ of these time series, so that flux at cadence $i$ is
+This method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters, and was applied to Aldebaran with further developments by \citet{Farr2018}.
+Because SAP is not possible, we consider instead the unsaturated pixels $p_j$ at the wings of the broad and structured PSF.
+We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux at cadence $i$ is
 
@@
 
-\noindent The weights are chosen to minimize an objective function
+\noindent In our updated pipeline presented here, the weights are chosen to minimize an objective function
 
@@
 \noindent which is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$.
-For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation as used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
-The lag parameter $l$ allow for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.
+For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
+The lag parameter $l$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.
 The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise.
@@
 On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for all values of $k$ and improves very slowly with $l$ for longer lags.
-In calculating lightcurves here, seeing the very weak dependence of short cadence CDPP on $l$, we calculate our final light curves with TV and a lag of 300 cadences for consistency with the long cadence method.
 
@@
 % link to tables
-% normal apertures in 6
 
@@
 While some very bright stars were observed with conventional apertures as part of these programs, simple aperture photometry is satisfactory on these targets and we exclude them from the present discussion and data release, which is oriented strictly towards targets only observable with halo photometry.
+% normal apertures in 6
 We make an exception for Spica, which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture.
@@
 
-Some of the objects here have been previously published, but we here provide the first public data releases for the Pleiades' Seven Sisters \citep{White2017}, Aldebaran \citep{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{Arentoft2019}, as well as $\rho$~Leo with halo photometry but without using the TV-min method \citep{Aerts2018}.
+Analyses for several of the objects here have been previously published, but we here provide the first public data releases for the Pleiades' Seven Sisters \citep{White2017}, Aldebaran \citep{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{Arentoft2019}, as well as $\rho$~Leo which was studied with halo pixels but without our objective functions \citep{Aerts2018}.
 

### 2019-04-05 paper/ms.tex
figure caption

@@
 \plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.pdf}
-\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis.}
+\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis.
+The top three panels illustrate \textsc{k2sc} systematics correction: at the top, flux minus the GP time trend (blue dots) with GP $x,y$ trend superimposed (orange line); in the middle, flux minus GP $x,y$ components with GP time trend superimposed, and in green, a fifteenth-order polynomial trend; at the bottom the `whitened' light curve with flux minus both GP components.
+Middle two panels: log-flux map (left) and halo log-weight map (right).
+Bottom two panels: periodograms in linear (top) and log (bottom) units of the residuals of the corrected light curve minus the long term polynomial trend.
+Plots of this form are available in supplementary online material for all long-cadence stars, and similar plots for all short-cadence stars.}
 \end{figure*}

### 2019-04-05 paper/ms.tex
k2sc

@@
 Bottom two panels: periodograms in linear (top) and log (bottom) units of the residuals of the corrected light curve minus the long term polynomial trend.
-Plots of this form are available in supplementary online material for all long-cadence stars, and similar plots for all short-cadence stars.}
+Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}.}
 \end{figure*}

### 2019-04-05 paper/ms.tex
formatting

@@
 % describe saturation
-The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30~min) and short (1~min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}.
+The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}.
 Beyond this point, additional photons cause excess electrons to `bleed' into adjacent pixels in both directions along the column containing the bright star.
@@
 In order to correct these, we employ the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$.
-The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction in space evaluated for fixed time represents the pointing systematics and is subtracted from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
+The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction for the $x,y$ component evaluated for fixed time represents the pointing systematics.
+We subtract the systmatics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
 The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112.

### 2019-04-05 paper/ms.tex
text updates

@@
 % added by DH
+\usepackage{xspace}
+
 \newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
@@
 % how well did we do?
-
-% interesting EB
+\textcolor{red}{How well do we do? How do we quantify our lightcurve SNR?}
 
 % RGs, Classical pulsators 
+\textcolor{red}{Variability catalog?}
+
+% interesting EB - 98 Tau
+The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity.
+We detect variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star with a period of 1.74\,d.
+This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star imply an 0.3 \rsun companion, almost certainly of stellar mass.
+With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.
 

### 2019-04-05 scripts/correct_halo.py

@@ -63,7 +63,7 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     frequency, power, spower = get_pgram(lc.time,lc.corr_flux-trend+np.nanmedian(trend),min_p=min_p,max_p=max_p)
     
     rc('axes', labelsize=7, titlesize=8)
-    rc('font', size=6)
+    rc('font', size=6, family="Times New Roman")
     rc('xtick', labelsize=7)
     rc('ytick', labelsize=7)
     rc('lines', linewidth=1)
@@ -71,9 +71,9 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     gs1 = GridSpec(3,2)
     gs1.update(top=0.95, bottom = 2/3.*1.05,hspace=0.0,left=0.09,right=0.96)
     gs2 = GridSpec(1,2)
-    gs2.update(top=2/3.*0.97,bottom=1/3.*1.07,hspace=0.35,left=0.09,right=0.96)
+    gs2.update(top=2/3.*1.01,bottom=1/3.*1.1,hspace=0.35,left=0.09,right=0.96)
     gs3 = GridSpec(2,2)
-    gs3.update(top=1/3.*0.96,bottom=0.04,hspace=0.07,left=0.09,right=0.96)
+    gs3.update(top=1/3.*1.01,bottom=0.04,hspace=0.225,left=0.09,right=0.96)
 
     ax_lctime = subplot(gs1[0,:])
     ax_lcpos = subplot(gs1[1,:],sharex=ax_lctime)

### 2019-04-05 paper/ms.tex
fonts

@@
 Bottom two panels: periodograms in linear (top) and log (bottom) units of the residuals of the corrected light curve minus the long term polynomial trend.
-Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}.}
+Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}.
+The period at maximum power (16\,d) is marked on all plots, though for $\rho$~Leonis all variability is consistent with red noise (Bowman et al., 2019).
+}
 \end{figure*}

### 2019-04-05 scripts/correct_halo.py

@@ -61,7 +61,8 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     poly = np.poly1d(np.polyfit(lc.time[m],lc.corr_flux[m],15))
     trend = poly(lc.time)
     frequency, power, spower = get_pgram(lc.time,lc.corr_flux-trend+np.nanmedian(trend),min_p=min_p,max_p=max_p)
-    
+    font = {'fontname':'Times New Roman'}
+
     rc('axes', labelsize=7, titlesize=8)
     rc('font', size=6, family="Times New Roman")
     rc('xtick', labelsize=7)
@@ -73,7 +74,7 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     gs2 = GridSpec(1,2)
     gs2.update(top=2/3.*1.01,bottom=1/3.*1.1,hspace=0.35,left=0.09,right=0.96)
     gs3 = GridSpec(2,2)
-    gs3.update(top=1/3.*1.01,bottom=0.04,hspace=0.225,left=0.09,right=0.96)
+    gs3.update(top=1/3.*1.01,bottom=0.04,hspace=0.23,left=0.09,right=0.96)
 
     ax_lctime = subplot(gs1[0,:])
     ax_lcpos = subplot(gs1[1,:],sharex=ax_lctime)
@@ -91,7 +92,7 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     plot_pgram(ax_periodogram,frequency,power,spower,formal_name)        
     plot_log_pgram(ax_logpgram,frequency,power,spower,formal_name)  
 
-    fig.suptitle(formal_name,y=0.99,fontsize=20)
+    fig.suptitle(formal_name,y=0.99,fontsize=20,**font)
     ax_periodogram.set_title('Periodograms')
     ax_fluxmap.set_title('Flux Map')
     ax_weightmap.set_title('TV-Min Weight Map')

### 2019-04-05 paper/ms.tex
fixes

@@
 \affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+
 \author[0000-0001-9879-9313]{Tabetha Boyajian}
@@
 Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}.
-The period at maximum power (16\,d) is marked on all plots, though for $\rho$~Leonis all variability is consistent with red noise (Bowman et al., 2019).
-}
+The period at maximum power (16\,d) is marked on all plots, though for $\rho$~Leonis all variability is consistent with red noise (Bowman et al., 2019).}
 \end{figure*}

### 2019-04-05 paper/ms.tex
quality flags

@@
 We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out.
-\textcolor{red}{More here from Tim.}
+\textcolor{red}{More here from Tim.} Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion.
+We now iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
 

### 2019-04-05 paper/ms.tex
abstract

@@
 While the \kepler\ mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars which saturate the detector are nevertheless some of the most interesting because of the ease with which they can be observed by other instruments and the wealth of knowledge about them that is already available.
-By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign 6 onwards.
+By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
 This halo campaign reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.

### 2019-04-06 paper/ms.tex
farr says any lag is ok

@@
 
-\title{The K2 Halo Photometry Campaign}
+\title{The K2 Halo Campaign}
 
@@
 The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise.
-TV is a convex objective function \textcolor{red}{and I think the generalizations are too} and $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
+TV with any lag is a convex objective function and $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
 

### 2019-05-02 paper/ms.tex
normalization
bright stars instead of halo to avoid confusion with galactic structure

@@
 %% this information may be modified by the editorial offices.
-\shorttitle{The K2 Halo Campaign}
+\shorttitle{The K2 Bright Star Survey}
 \shortauthors{B. J. S. Pope et al.}
@@
 
-\title{The K2 Halo Campaign}
+\title{The K2 Bright Star Survey}
 
@@
 By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
-This halo campaign reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
-Here we describe our pipeline, and present a catalogue of the halo sources, with classifications and parametrizations of their variability and remarks on interesting objects.
+This bright star survey reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
+Here we describe our pipeline, and present a catalogue of the bright stars studied, with classifications and parametrizations of their variability and remarks on interesting objects.
 These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST).
@@
 \begin{equation}
-    \Lambda_{k,l} \equiv \frac{\sum_i{|f_i - f_{i-l}|^k}}{\sum_i {f_i}},
+    \Lambda_{k,l} \equiv \frac{\sum_i{|f_i - f_{i-l}|^k}}{(\sum_i {f_i})^k},
 \end{equation}
@@
 In this context we can understand the optimum as TV-min suppressing systematics on the same timescale as they occur.
-On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for all values of $k$ and improves very slowly with $l$ for longer lags.
+On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ and improves very slowly with $l$ for longer lags, and performs very poorly for $k=3$ at all lags.
 
@@
 for objective function $\Lambda_{1,10}$.
-For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1, L2 or~L3 norms.}
+For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1 and L2~norms, while L3 performs poorly.}
 \label{cdpps}

### 2019-05-03 data/normal/get_c6_lcs.sh
download lcs

@@ -1,0 +1,1754 @@
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/70000/ktwo212270340-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/70000/ktwo212270773-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/70000/ktwo212270861-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/71000/ktwo212271587-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/71000/ktwo212271980-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/72000/ktwo212272120-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/73000/ktwo212273312-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/73000/ktwo212273454-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/75000/ktwo212275087-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/75000/ktwo212275195-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/75000/ktwo212275451-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/76000/ktwo212276317-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/76000/ktwo212276489-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/76000/ktwo212276968-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/77000/ktwo212277232-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/77000/ktwo212277440-c06_llc.fits
+curl -O https://archive.stsci.edu/missions/k2/lightcurves/c6/212200000/78000/ktwo212278489-c06_llc.fits
[…]

### 2019-05-04 scripts/sbatch_unsaturated.sh
unsaturated

@@ -1,0 +1,26 @@
+#!/bin/bash
+
+#SBATCH --job-name=Array1d
+#SBATCH --nodes=1
+#SBATCH --cpus-per-task=1
+#SBATCH --mem=8GB
+#SBATCH --time=08:00:00
+#SBATCH --array=0-1754
+
+if [ "$SLURM_ARRAY_TASK_ID" == "" ]; then exit; fi
+
+i=0
+while read -r line; do
+    if [ $i -eq $SLURM_ARRAY_TASK_ID ]; then
+
+		module purge
+		module load anaconda3/5.3.1
+		source ~/pyenv/py3.7.0/bin/activate
+
+        eval $line 
+        exit
+    fi
+    i=$((i+1))
+done < sbatch_unsaturated.txt
+
+exit

### 2019-05-04 scripts/sbatch_unsaturated2.sh
new lengths

@@ -5,7 +5,7 @@
 #SBATCH --cpus-per-task=1
 #SBATCH --mem=8GB
 #SBATCH --time=08:00:00
-#SBATCH --array=0-850
+#SBATCH --array=0-905
 
 if [ "$SLURM_ARRAY_TASK_ID" == "" ]; then exit; fi
 
@@ -21,6 +21,6 @@ while read -r line; do
         exit
     fi
     i=$((i+1))
-done < sbatch_unsaturated.txt
+done < sbatch_unsaturated2.txt
 
 exit

### 2019-05-05 scripts/correct_unsaturated.py
correct unsaturated

@@ -1,0 +1,195 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+import matplotlib 
+import matplotlib as mpl
+from matplotlib import rc
+from matplotlib.gridspec import GridSpec
+from matplotlib.pyplot import figure, subplots, subplot
+from mpl_toolkits.axes_grid1 import make_axes_locatable, axes_size
+
+import lightkurve 
+from lightkurve import KeplerLightCurve, KeplerTargetPixelFile
+from lightkurve.convenience import estimate_cdpp
+from k2sc.standalone import k2sc_lc
+import k2sc
+
+import warnings ## eeek!
+warnings.filterwarnings("ignore")
+
+import halophot
+from halophot.halo_tools import *
+
+from astropy.table import Table
+from astropy.io import fits
+
+import fitsio
+
+from argparse import ArgumentParser
+
+mpl.style.use('seaborn-colorblind')
+
+#To make sure we have always the same matplotlib settings
+#(the ones in comments are the ipython notebook settings)
+
+mpl.rcParams['figure.figsize']=(8.0,6.0)    #(6.0,4.0)
+mpl.rcParams['font.size']=18               #10 
+mpl.rcParams['savefig.dpi']= 200             #72 
+mpl.rcParams['axes.labelsize'] = 16
+mpl.rcParams['axes.labelsize'] = 16
+mpl.rcParams['xtick.labelsize'] = 12
+mpl.rcParams['ytick.labelsize'] = 12
+mpl.rcParams["font.family"] = "Times New Roman"
+
+
+'''-----------------------------------------------------------------
+correct_halo.py
+
+This executable Python script allows you to detrend any single object 
+made using halophot with k2sc
+
+-----------------------------------------------------------------'''
+
+def match_cadences(halocads,lccads):
+    indices =np.array([1 if j in lccads else 0 for j in halocads])
+    return np.where(indices==1)[0]
+
+def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
+    min_p,max_p=1./24.,20.
+
+    PW,PH = 8.27, 11.69
+    m = np.isfinite(lc.corr_flux)
[…]

### 2019-05-05 scripts/reduce_unsaturated.py
reduce unsaturated

@@ -1,0 +1,15 @@
+import glob
+from astropy.table import Table 
+from tqdm import tqdm
+
+files = glob.glob('epic_*.txt')
+
+with open('all_epics.txt','w') as f:
+
+	f.write('epic, cdpp_sap, cdpp_pdc, cdpp_k2sc_pdc, cdpp_halo, cdpp_k2sc_halo, enclosed_weight\n')
+
+	for fname in tqdm(files):
+		s = open(fname,'r').read()
+		f.write(s+'\n')
+
+print('Done!')

### 2019-05-05 scripts/reduce_unsaturated.py
commas

@@ -9,7 +9,7 @@ with open('all_epics.txt','w') as f:
 	f.write('epic, cdpp_sap, cdpp_pdc, cdpp_k2sc_pdc, cdpp_halo, cdpp_k2sc_halo, enclosed_weight\n')
 
 	for fname in tqdm(files):
-		s = open(fname,'r').read()
+		s = open(fname,'r').read().replace(' ',', ')
 		f.write(s+'\n')
 
 print('Done!')

### 2019-05-06 scripts/correct_unsaturated.py
fixes

@@ -54,18 +54,46 @@ def match_cadences(halocads,lccads):
     indices =np.array([1 if j in lccads else 0 for j in halocads])
     return np.where(indices==1)[0]
 
-def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
+def plot_weightmap_overlay(ax1,weightmap,name,title=False,mask=None):
+        norm = np.size(weightmap)
+
+        cmap = mpl.cm.seismic
+        cmap.set_bad('k',1.)
+
+        im = np.log10(weightmap.T*norm)
+        pic = ax1.imshow(im.T,cmap=cmap, vmin=-2*np.nanmax(im),vmax=2*np.nanmax(im),
+            interpolation='nearest',origin='lower')        
+        if [mask] != None:
+            mask_show = np.ma.masked_array(np.zeros_like(mask),mask=(mask))
+            ax1.imshow(mask_show,cmap=mpl.cm.gray,alpha=0.3)
+
+        if title:
+            plt.title(r'TV-min Weightmap %s' % name)
+
+        # cbaraxes, kw = mpl.colorbar.make_axes(ax1,location='right',pad=0.01)
+        # plt.colorbar(pic,cax=cbaraxes)
+
+        # cbaraxes.yaxis.set_ticks_position('right')
+        aspect = 20
+        pad_fraction = 0.5
+
+        divider = make_axes_locatable(ax1)
+        width = axes_size.AxesY(ax1, aspect=1./aspect)
+        pad = axes_size.Fraction(pad_fraction, width)
+        cax = divider.append_axes("right", size=width, pad=pad)
+        plt.colorbar(pic, cax=cax)
+
+        ax1.yaxis.set_ticks_position('left')        
+
+def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test',mask=None):
     min_p,max_p=1./24.,20.
 
     PW,PH = 8.27, 11.69
-    m = np.isfinite(lc.corr_flux)
-    poly = np.poly1d(np.polyfit(lc.time[m],lc.corr_flux[m],15))
-    trend = poly(lc.time)
-    frequency, power, spower = get_pgram(lc.time,lc.corr_flux-trend+np.nanmedian(trend),min_p=min_p,max_p=max_p)
[…]

### 2019-05-06 scripts/reduce_unsaturated.py

@@ -6,7 +6,7 @@ files = glob.glob('epic_*.txt')
 
 with open('all_epics.txt','w') as f:
 
-	f.write('epic, cdpp_sap, cdpp_pdc, cdpp_k2sc_pdc, cdpp_halo, cdpp_k2sc_halo, enclosed_weight\n')
+	f.write('epic, Kp, cdpp_sap, cdpp_pdc, cdpp_k2sc_pdc, cdpp_halo, cdpp_k2sc_halo, enclosed_weight\n')
 
 	for fname in tqdm(files):
 		s = open(fname,'r').read().replace(' ',', ')

### 2019-05-06 paper/ms.tex
farr and hogg on author list

@@
 
+\author[0000-0003-1540-8562]{Will M. Farr}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
+\affiliation{Department of Physics and Astronomy, Stony Brook University, Stony Brook, NY 11794, USA}
+
+\author[0000-0003-2866-9403]{David W. Hogg}
+\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
+\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
+\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"{o}nigstuhl 17, D-69117 Heidelberg}
+\affiliation{Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
+
 \author[0000-0001-8832-4488 ]{Daniel Huber}
@@
 
-We would like to thank Will Farr for his very helpful comments on the halo method.
-
 This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.

### 2019-05-06 paper/ms.tex
new version of the objective function

@@
 \usepackage{xspace}
+\usepackage{amsmath}
 
@@
 \begin{equation}
-    \Lambda_{k,l} \equiv \frac{\sum_i{|f_i - f_{i-l}|^k}}{(\sum_i {f_i})^k},
+    \Lambda_{k,l} \equiv {\sum_i{|f_i - f_{i-l}|^k}},
 \end{equation}
 
-\noindent which is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$.
+\noindent subject to th the constraints
+
+\begin{align}
+\forall_j w_j &> 0\\
+\sum_i f_i  &= N
+\end{align}
+
+$\Lambda_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$.
 For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
+The $L=2$ L2 Variation (L2V) is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse.
 The lag parameter $l$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.

### 2019-05-06 paper/ms.tex
new version of the objective function

@@
 
-\noindent subject to th the constraints
+\noindent subject to the constraints
 
@@
 
-$\Lambda_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$.
+This is a classic linear convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code.
+$\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
+
+The objective function $\Lambda_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$.
 For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
@@
 The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise.
-TV with any lag is a convex objective function and $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
 

### 2019-05-06 paper/ms.tex
l-bfgs-b optimization code

@@
 
-This is a classic linear convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code.
+This is a classic linear convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}.
 $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.

### 2019-05-06 paper/ms.tex
rearrange and rephrase a bit

--- 2019-05-06 paper/ms.tex
@@
 It was therefore necessary to develop a method to recover good light curves from a smaller number of unsaturated pixels in a compact aperture around bright stars: halo photometry.
+% smear
+This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
+While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.
 
@@
 
-This is a classic linear convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code.
+This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}.
 $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
@@
 
-% smear
-This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
-While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.
+Unlike other methods for calibrating \kepler systematics, other than the value of $l$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
+The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
 

### 2019-05-06 paper/ms.tex
something in the abstract
formatting

@@
 \affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
+\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
 \affiliation{NASA Sagan Fellow}
@@
 By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
+The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars.
 This bright star survey reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
@@
 \forall_j w_j &> 0\\
-\sum_i f_i  &= N
+\sum_{i=1}^{N} f_i  &= N
 \end{align}
@@
 For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
-The $L=2$ L2 Variation (L2V) is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse.
+The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse.
 The lag parameter $l$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.

### 2019-05-06 paper/ms.tex
okina

@@
 \usepackage{amsmath}
+\usepackage{newunicodechar,graphicx}
+
+\DeclareRobustCommand{\okina}{%
+  \raisebox{\dimexpr\fontcharht\font`A-\height}{%
+    \scalebox{0.8}{`}%
+  }%
+}
+\newunicodechar{ʻ}{\okina}
 
@@
 \author[0000-0001-8832-4488 ]{Daniel Huber}
-\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
+\affiliation{Institute for Astronomy, University of Hawai\okina i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
 \affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
@@
 
-Unlike other methods for calibrating \kepler systematics, other than the value of $l$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
-The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
-
 % benchmarking with lags and objective functions
 
-In order to choose the objective function $\Lambda_{k,l}$, we have selected the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the halo sample and one with very little high frequency variability detected or predicted, which was also observed at short cadence.
+In order to choose the values for $k$ and $l$ in our objective function, we have selected the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the halo sample and one with very little high frequency variability detected or predicted, which was also observed at short cadence.
 We choose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better.
@@
 
+%  improvements
+Unlike other methods for calibrating \kepler systematics, other than the value of $l$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
+The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
+It is therefore likely that significant improvements can be made to the method by including cotrending basis vectors with mean zero and whose weights are allowed to be negative, which would represent systematics which are common to all pixels in the halo aperture and therefore masquerade as signal.
+Any linear combination of convex objective functions is itself convex, and future extensions to the method could enforce combinations of different lags and orders to better represent systematics occurring on different timescales (e.g.
+thruster firings, red noise) and with different levels of smoothness.
+
 % describe changes with respect to Pleiades and Aldebaran papers: deathstar
 
-In addition to these changes in objective function, we have also added a feature `\texttt{deathstar}' to deal with contamination.
+In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination.
 We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out.

### 2019-05-07 paper/ms.tex
bit about softmax

@@
 $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
+In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.
 

### 2019-05-09 paper/ms.tex
misc updates

@@
 \begin{abstract}
-While the \kepler\ mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars which saturate the detector are nevertheless some of the most interesting because of the ease with which they can be observed by other instruments and the wealth of knowledge about them that is already available.
-By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
+While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars, which saturate the detector, are important because they can be and have been observed by other instruments at very high signal-to-noise ratio.
+By considering the unsaturated scattered light `halo' around these stars we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
 The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars.
-This bright star survey reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
+The key methodology is to optimize the weights of a linear combination of pixel time series with respect to an objective function.
+We test a range of such objective functions, finding that generalizations of Total Variation perform well on both saturated and unsaturated \ktwo targets.
+Applying this to the bright stars across the \ktwo Campaigns, this reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
 Here we describe our pipeline, and present a catalogue of the bright stars studied, with classifications and parametrizations of their variability and remarks on interesting objects.
@@
 
+% describe saturation
+The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}.
+For objects brighter than this, additional photons create excess electrons which `bleed' into adjacent pixels in both directions along the column containing the bright star.
+Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit of stars as bright as 16~Cyg~AB, $\theta$~Cyg and RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}.
+In the nominal \kepler mission this was not attempted for all such bright stars, and in \ktwo, the several-pixel spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.
+While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is rendered impossible for the very brightest stars whose bleed columns may run to the edge of the detector.
+Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo.
+
 % briefly intro the halo method and halo literature
-In order to recover precise photometry of the brightest stars in \ktwo, we have developed two main approaches, `smear' and `halo' photometry.
-Smear photometry \citep{Pope2016} uses collateral calibration data to recover light curves of stars which were not necessarily conventionally targeted.
+In order to recover precise photometry of the brightest stars in \ktwo, we have therefore developed two main approaches, `smear' and `halo' photometry.
+Smear photometry \citep{Pope2016} uses collateral `smear' calibration data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
+This can be processed recover light curves of stars which were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns.
+The main disadvantage of this method is that it confuses all stars in the same column, which means that in crowded fields smear light curves tend to be significantly contaminated.
+
+% halo
 The more precise method of halo photometry, which is the subject of this paper, uses the broad `halo' of scattered light around a saturated star to recover relative photometry, by constructing a light curve as a linear combination of individual pixel time series and minimizing a Total Variation objective function (TV-min).
@@
 Unlike smear, this requires downloading data out to a 12--20~pixel radius around each star, and has accordingly only been possible for stars that were specifically targeted with apertures optimized for this method and for a small number of other stars for which this is fortuitously the case.
+The pixel requirements for this are sufficiently low that, with the help of the \ktwo Guest Observer office, such apertures were obtained for most of the bright targets from Campaign~4 onwards.
 
 % describe contents of paper: code, catalog, categorization, conclusions
-In this Paper we describe the complete catalog of long-cadence \ktwo halo light curves which we have made publicly available.
+In this Paper we describe numerical experiments testing the TV-min method and extending it to generalizations with different exponents and timescales.
+We show that the method as previously employed applying standard TV-min is suboptimal, and gain a modest improvement from taking finite differences close to the timescale of \ktwo thruster firings.
+We go on to present complete catalog of long-cadence \ktwo halo light curves, which we have made publicly available.
 We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability.
@@
 \label{method}
-
-% describe saturation
-The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}.
-Beyond this point, additional photons cause excess electrons to `bleed' into adjacent pixels in both directions along the column containing the bright star.
-This process occurs conservatively and simple aperture photometry (SAP) adding all the flux contained in a window around the bleed column has recovered light curves with precisions close to the photon noise limit of stars as bright as 16~Cyg~AB, $\theta$~Cyg and RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}.
-In the nominal \kepler mission this was not attempted for all such bright stars, and in \ktwo, the several-pixel spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.
-While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is rendered impossible for the very brightest stars whose bleed columns may run to the edge of the detector.
-Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo.
-It was therefore necessary to develop a method to recover good light curves from a smaller number of unsaturated pixels in a compact aperture around bright stars: halo photometry.
-% smear
-This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
-While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.
 
@@
 \begin{equation}
-    \Lambda_{k,l} \equiv {\sum_i{|f_i - f_{i-l}|^k}},
+    Q_{k,l} \equiv {\sum_i{|f_i - f_{i-\delta}|^k}},
 \end{equation}
@@
 \forall_j w_j &> 0\\
-\sum_{i=1}^{N} f_i  &= N
+\sum_{i=1}^{N} f_i  &= N.
 \end{align}
@@
 This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}.
-$\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
+$Q_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
 In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.
 
-The objective function $\Lambda_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$.
-For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
+The objective function $Q_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $\delta$.
+For $k = 1$ and $\delta = 1$, $Q_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
 The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse.
-The lag parameter $l$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.
+The lag parameter $\delta$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.
 The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise.
+For convenience in the rest of this paper, we will refer to the $k=1$ case as TV, the $k=2$ case as L2V, and the $k=3$ case as L3V.
 
@@
 
-In order to choose the values for $k$ and $l$ in our objective function, we have selected the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the halo sample and one with very little high frequency variability detected or predicted, which was also observed at short cadence.
+In order to choose the values for $k$ and $\delta$ in our objective function, we have selected the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the sample of stars with halo apertures, and one with very little high frequency variability detected or predicted, which was also observed at short cadence.
 We choose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better.
-We calculate halo lightcurves and their CDPPs for $k \in \{1,2,3\}$, and $l \in [1,50]$ for long cadence and (sparsely) $l \in [1,2500]$ for short cadence data.
+We calculate halo lightcurves and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data.
 The results are displayed in Figure~\ref{cdpps}.
-We find that for long cadence data, the L1 norm (TV) and a lag of 10 provide the best CDPP, which is unsurprising given that this is a slightly shorter lag than the 12~cadence thruster firing period.
-In this context we can understand the optimum as TV-min suppressing systematics on the same timescale as they occur.
-On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ and improves very slowly with $l$ for longer lags, and performs very poorly for $k=3$ at all lags.
+We find that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP.
+This is unsurprising: that this is one cadence shorter than the 12~cadence thruster firing period.
+In this context we can understand the optimum as suppressing systematics on the same timescale as they occur.
+On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.
+
+% \begin{figure*}
+% \plottwo{lag_lc_cdpp.pdf}{lag_sc.pdf}
+% \caption{Behaviour of long cadence (left) and short cadence (right) 6.5~hour CDPP for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$.
+For long cadence this shows a minimum for L1 norm and $\delta=10$, i.e.
+for objective function $Q_{1,10}$.
+For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1 and L2~norms, while L3 performs poorly.}
+% \label{cdpps}
+% \end{figure*}
 
 \begin{figure*}
-\plottwo{lag_lc_cdpp.pdf}{lag_sc.pdf}
-\caption{Behaviour of long cadence (left) and short cadence (right) 6.5~hour CDPP for the quiet dwarf 36~Ophiuchi as a function of lag parameter $l$.
-For long cadence this shows a minimum for L1 norm and $l=10$, i.e.
-for objective function $\Lambda_{1,10}$.
-For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1 and L2~norms, while L3 performs poorly.}
+\plottwo{lag_lc_cdpp.pdf}{lag_lc_sys.pdf}
+\caption{Behaviour of long cadence 6.5~hour CDPP (left) and $4 c/d$ systematics power (right) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$.
+CDPP shows a minimum for L1 norm and $\delta=10$, i.e.
+for objective function $Q_{1,10}$.}
 \label{cdpps}
@@
 
+\begin{figure}
+\plotone{lag_sc.pdf}
+\caption{Behaviour of short cadence 6.5~hour CDPP for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$.
+CDPP continuously improves for higher lags and shows no strong differences between L1 and L2~norms, while L3 performs poorly.}
+\label{cdpps}
+\end{figure}
+
 %  improvements
-Unlike other methods for calibrating \kepler systematics, other than the value of $l$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
+Unlike other methods for calibrating \kepler systematics, other than the value of $\delta$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
 The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
@@
 The sample of K2 bright stars presented here only includes those with halo apertures, but while some others are available conventionally, many were not assigned target pixels and were not downloaded at all.
-Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., in prep.), and this can also be done in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more difficult.
+Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., in prep.), and this can also be done in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more challenging.
 A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.

### 2019-05-09 paper/ms.tex
hogg comments

@@
 The objective function $Q_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $\delta$.
-For $k = 1$ and $\delta = 1$, $Q_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
+For $k = 1$ and $\delta = 1$, $Q_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers \citep[e.g.][]{White2017,Farr2018}, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.
 The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse.
@@
 
+% \begin{figure*}
+% \plottwo{lag_lc_cdpp.pdf}{lag_lc_sys.pdf}
+% \caption{Behaviour of long cadence 6.5~hour CDPP (left) and $4 c/d$ systematics power (right) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$.
+CDPP shows a minimum for L1 norm and $\delta=10$, i.e.
+for objective function $Q_{1,10}$.}
+% \label{cdpps}
+% \end{figure*}
+
 \begin{figure*}
-\plottwo{lag_lc_cdpp.pdf}{lag_lc_sys.pdf}
-\caption{Behaviour of long cadence 6.5~hour CDPP (left) and $4 c/d$ systematics power (right) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$.
+\plotone{lag_opt_both.pdf}
+\caption{Behaviour of long cadence 6.5~hour CDPP (bottom) and $4 c/d$ systematics power (top) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$.
 CDPP shows a minimum for L1 norm and $\delta=10$, i.e.

### 2019-05-09 paper/ms.tex

@@
 CDPP shows a minimum for L1 norm and $\delta=10$, i.e.
-for objective function $Q_{1,10}$.}
+for objective function $Q_{1,10}$, which is marked with a blue dashed vertical line.
+This does not correspond to an optimum in systematic power, which is slightly lower for smaller $\delta$.
+Nevertheless, we have chosen $\delta=10$ for the light curves in this catalog because of its improvement in overall CDPP as a measure of planet detection efficiency and overall light curve quality.}
 \label{cdpps}

### 2019-05-10 scripts/sbatch_unsaturated2.sh
new target list

@@ -5,7 +5,7 @@
 #SBATCH --cpus-per-task=1
 #SBATCH --mem=8GB
 #SBATCH --time=08:00:00
-#SBATCH --array=0-905
+#SBATCH --array=0-750
 
 if [ "$SLURM_ARRAY_TASK_ID" == "" ]; then exit; fi
 

### 2019-05-10 scripts/sbatch_unsaturated3.sh

@@ -5,7 +5,7 @@
 #SBATCH --cpus-per-task=1
 #SBATCH --mem=8GB
 #SBATCH --time=08:00:00
-#SBATCH --array=0-999
+#SBATCH --array=0-717
 
 if [ "$SLURM_ARRAY_TASK_ID" == "" ]; then exit; fi
 
@@ -21,6 +21,6 @@ while read -r line; do
         exit
     fi
     i=$((i+1))
-done < sbatch_unsaturated.txt
+done < sbatch_unsaturated3.txt
 
 exit

### 2019-05-10 scripts/sbatch_unsaturated.sh
rebalance

@@ -5,7 +5,7 @@
 #SBATCH --cpus-per-task=1
 #SBATCH --mem=8GB
 #SBATCH --time=08:00:00
-#SBATCH --array=0-999
+#SBATCH --array=0-922
 
 if [ "$SLURM_ARRAY_TASK_ID" == "" ]; then exit; fi
 

### 2019-05-10 scripts/sbatch_unsaturated2.sh

@@ -5,7 +5,7 @@
 #SBATCH --cpus-per-task=1
 #SBATCH --mem=8GB
 #SBATCH --time=08:00:00
-#SBATCH --array=0-750
+#SBATCH --array=0-828
 
 if [ "$SLURM_ARRAY_TASK_ID" == "" ]; then exit; fi
 

### 2019-05-10 scripts/sbatch_unsaturated3.sh
tables and stuff

@@ -4,7 +4,7 @@
 #SBATCH --nodes=1
 #SBATCH --cpus-per-task=1
 #SBATCH --mem=8GB
-#SBATCH --time=08:00:00
+#SBATCH --time=00:25:00
 #SBATCH --array=0-717
 
 if [ "$SLURM_ARRAY_TASK_ID" == "" ]; then exit; fi

### 2019-05-10 scripts/sbatch_test.sh
font test

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+#SBATCH --nodes=1
+#SBATCH --cpus-per-task=1
+#SBATCH --mem=8GB
+#SBATCH --time=00:25:00
+
+python test_font.py 
+
+exit

### 2019-05-10 scripts/test_font.py

@@ -1,0 +1,23 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+mpl.rcParams['figure.figsize']=(8.0,6.0)    #(6.0,4.0)
+mpl.rcParams['font.size']=18               #10 
+mpl.rcParams['savefig.dpi']= 200             #72 
+mpl.rcParams['axes.labelsize'] = 16
+mpl.rcParams['axes.labelsize'] = 16
+mpl.rcParams['xtick.labelsize'] = 12
+mpl.rcParams['ytick.labelsize'] = 12
+mpl.rcParams["font.family"] = "Times New Roman"
+
+x = np.linspace(0,1,100)
+
+y = x**2
+
+plt.plot(x,y,'.')
+
+plt.xlabel('x label')
+plt.ylabel('y label')
+plt.title('font test')
+
+plt.savefig('font_test.png')

### 2019-05-10 scripts/test_font.py
font test

@@ -1,5 +1,6 @@
 import numpy as np
 import matplotlib.pyplot as plt
+import matplotlib as mpl
 
 mpl.rcParams['figure.figsize']=(8.0,6.0)    #(6.0,4.0)
 mpl.rcParams['font.size']=18               #10 

### 2019-05-14 paper/ms.tex
tables and stuff
red giant asteroseismology now included

@@
 \usepackage{newunicodechar,graphicx}
+\usepackage{longtable}
 
@@
 We calculate halo lightcurves and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data.
-The results are displayed in Figure~\ref{cdpps}.
+The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}.
 We find that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP.
@@
 Nevertheless, we have chosen $\delta=10$ for the light curves in this catalog because of its improvement in overall CDPP as a measure of planet detection efficiency and overall light curve quality.}
-\label{cdpps}
+\label{cdpps_lc}
 \end{figure*}
@@
 CDPP continuously improves for higher lags and shows no strong differences between L1 and L2~norms, while L3 performs poorly.}
-\label{cdpps}
+\label{cdpps_sc}
 \end{figure}
@@
 
-The full sample of stars for which halo apertures were obtained is listed in Tables~\ref{table_0}--\ref{table_5}, broken down by Campaign.
+The full sample of stars for which halo apertures were obtained is listed in Table~\ref{table_all}.
 While some very bright stars were observed with conventional apertures as part of these programs, simple aperture photometry is satisfactory on these targets and we exclude them from the present discussion and data release, which is oriented strictly towards targets only observable with halo photometry.
@@
 
-This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{scipy}; \texttt{lightkurve} \citep{lightkurve}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.
+This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France.
 Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
@@
 Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.
+We acknowledge the support of the Group of Eight universities and the German Academic Exchange Service through the Go8 Australia-Germany Joint Research Co-operation Scheme.
+
+\software{IPython  \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}
 
@@
 \newpage
+\appendix
 % \section*{Sample}
 
-\input{all_stars_1}
-\input{all_stars_2}
-\input{all_stars_3}
-\input{all_stars_4}
-\input{all_stars_5}
-\input{all_stars_6}
-
+% \input{all_stars_1}
+% \input{all_stars_2}
+% \input{all_stars_3}
+% \input{all_stars_4}
+% \input{all_stars_5}
+% \input{all_stars_6}
+\input{table_all}
+\input{rgs}
 %% This command is needed to show the entire author+affilation list when

### 2019-05-14 paper/ms.tex

@@
 
+\subsection{Oscillating Red Giants}
+\label{sec:rgs}
+31 of the evolved stars in our sample have detectable stochastically-excited solar-like acoustic oscillations.
+In the asymptotic limit, these consist of a comb of modes separated by the large frequency separation \Dnu, approximately the sound-crossing-time of the star, with a Gaussian envelope centred on the frequency of maximum power \numax, which scales with the acoustic cutoff frequency at the star's surface.
+These can be used to constrain stellar fundamental parameters, and detailed studies of the deviations from this asymptotic limit for acoustic $p$-modes, for example due to their interaction with gravity-wave $g$-modes, can be used to accurately determine the stellar evolutionary state, for example to distinguish hydrogen shell burning red giant branch from helium core burning red clump stars.
+
+Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for all 31 giants for which oscillations are detected.
+These parameters are listed in Table~\ref{rgs}.
+High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models.
+This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J} and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).
+
 % RGs, Classical pulsators 
+\subsection{Classical Variables}
+\label{sec:variables}
 \textcolor{red}{Variability catalog?}
+
+\subsection{Chemically-Peculiar Stars}
 

### 2019-05-14 scripts/correct_unsaturated.py
trends

@@ -113,8 +113,8 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test',mask=None):
     ax_periodogram   = subplot(gs3[0,:])
     ax_logpgram    = subplot(gs3[1,:])
 
-    plot_lc(ax_lctime,lc.time,lc.flux-lc.tr_time+np.nanmedian(lc.tr_time),formal_name,trend=lc.tr_position)
-    plot_lc(ax_lcpos,lc.time,lc.flux-lc.tr_position+np.nanmedian(lc.tr_position),formal_name,trend=lc.tr_time)
+    plot_lc(ax_lctime,lc.time,lc.flux-lc.tr_time+np.nanmedian(lc.tr_time),formal_name,trends=[lc.tr_position])
+    plot_lc(ax_lcpos,lc.time,lc.flux-lc.tr_position+np.nanmedian(lc.tr_position),formal_name,trends=[lc.tr_time])
     plot_lc(ax_lcwhite,lc.time,lc.corr_flux-lc.tr_time,formal_name+': Whitened')
     plot_weightmap_overlay(ax_weightmap,weightmap,formal_name,mask=mask)
     plot_fluxmap(ax_fluxmap,image,formal_name)

### 2019-05-15 paper/ms.tex
fix syntax

@@
 % do hot star asteroseismology and red giants as benchmarks, interferometry
-Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.) and the Hyades giants (White et al., in prep.).
-In addition to this, we aim to separately publish asteroseismic catalogues of the red giants (Yu et al., in prep.) and main-sequence stars (Greklek-McKeon et al., in prep.).
+Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.), the Hyades giants (White et al., in prep.), and main-sequence stars (Greklek-McKeon et al., in prep.).
 
@@
 The sample of K2 bright stars presented here only includes those with halo apertures, but while some others are available conventionally, many were not assigned target pixels and were not downloaded at all.
-Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., in prep.), and this can also be done in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more challenging.
+Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., under review), and this can also be done in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more challenging.
 A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.

### 2019-05-15 scripts/correct_unsaturated.py

@@ -85,6 +85,20 @@ def plot_weightmap_overlay(ax1,weightmap,name,title=False,mask=None):
 
         ax1.yaxis.set_ticks_position('left')        
 
+def plot_lc(ax1,time,lc,name,trend=None,title=False):
+        m = (lc>0.) * (np.isfinite(lc))
+
+        ax1.plot(time[m],lc[m]/np.nanmedian(lc[m]),'.')
+        dt = np.nanmedian(time[m][1:]-time[m][:-1])
+        ax1.set_xlim(time[m].min()-dt,time[m].max()+dt)
+        if trend is not None:
+            ax1.plot(time[m],trend[m]/np.nanmedian(trend[m]),'-',color=colours[2])
+            plt.legend(labels=['Flux','Trend'])
+        ax1.set_xlabel('Time')
+        ax1.set_ylabel('Relative Flux')
+        if title:
+            plt.title(r'%s' % name)
+
 def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test',mask=None):
     min_p,max_p=1./24.,20.
 
@@ -113,11 +127,11 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test',mask=None):
     ax_periodogram   = subplot(gs3[0,:])
     ax_logpgram    = subplot(gs3[1,:])
 
-    plot_lc(ax_lctime,lc.time,lc.flux-lc.tr_time+np.nanmedian(lc.tr_time),formal_name,trends=[lc.tr_position])
-    plot_lc(ax_lcpos,lc.time,lc.flux-lc.tr_position+np.nanmedian(lc.tr_position),formal_name,trends=[lc.tr_time])
+    plot_lc(ax_lctime,lc.time,lc.flux-lc.tr_time+np.nanmedian(lc.tr_time),formal_name,trend=lc.tr_position)
+    plot_lc(ax_lcpos,lc.time,lc.flux-lc.tr_position+np.nanmedian(lc.tr_position),formal_name,trend=lc.tr_time)
     plot_lc(ax_lcwhite,lc.time,lc.corr_flux-lc.tr_time,formal_name+': Whitened')
     plot_weightmap_overlay(ax_weightmap,weightmap,formal_name,mask=mask)
-    plot_fluxmap(ax_fluxmap,image,formal_name)
+    plot_fluxmap(ax_fluxmap,np.exp(image),formal_name)
     plot_pgram(ax_periodogram,frequency,power,spower,formal_name)        
[…]

### 2019-05-15 scripts/correct_unsaturated.py
new version

@@ -220,6 +220,23 @@ if __name__ == '__main__':
         f.write('%s %f %f %f %f %f %f %f' %  (epic, lc_pdc.primary_header['kepmag'], cdpp_sap, cdpp_pdc, cdpp_k2sc_pdc, cdpp_halo, cdpp_k2sc_halo, enclosed_weight))
     print('Written data to epic_%s.txt' % epic)
 
+    to_save = ['time', 'flux', 'flux_err','centroid_col', 'centroid_row', 'quality', 'cadenceno','pos_corr1', 'pos_corr2','tr_position', 'tr_time','corr_flux']
+
+    dummy = fits.getheader('../data/normal/ktwo%s-c06_lpd-targ.fits.gz' % (epic)) # get the old header from the TPF
+    dummy['NAXIS']=1
+    dummy['halo'] =(halophot.__version__,'halophot version')
+    dummy['objective']=('tv','halophot objective')
+    dummy['sub']=(1,'halophot subsampling')
+    dummy['starname']=(epic,'Star Identifier')
+
+    hdu = fits.PrimaryHDU(weightmap,dummy) # can't save a masked array yet so just using pixelmap
+    cols = [fits.Column(name=key,format="D",array=lc_dummy.__dict__[key]) for key in to_save]
+    tab = fits.BinTableHDU.from_columns(cols)
+
+    hdul = fits.HDUList([hdu, tab])
+    hdul.writeto('../data/normal/hlsp_halo_k2_llc_%s_-c%s_kepler_v1_lc.fits' % (epic,campaign),overwrite=True)
+
+
     if args.do_plot:
         plot_k2sc(lc_out,np.nanmean(tpf.flux,axis=0),weightmap.T,formal_name='(EPIC %s) Detrended' % epic,mask=tpf.pipeline_mask,
             save_file='../data/normal/epic_%s.png' % (epic))

### 2019-05-16 scripts/correct_unsaturated.py
exp

@@ -131,7 +131,7 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test',mask=None):
     plot_lc(ax_lcpos,lc.time,lc.flux-lc.tr_position+np.nanmedian(lc.tr_position),formal_name,trend=lc.tr_time)
     plot_lc(ax_lcwhite,lc.time,lc.corr_flux-lc.tr_time,formal_name+': Whitened')
     plot_weightmap_overlay(ax_weightmap,weightmap,formal_name,mask=mask)
-    plot_fluxmap(ax_fluxmap,np.exp(image),formal_name)
+    plot_fluxmap(ax_fluxmap,(image),formal_name)
     plot_pgram(ax_periodogram,frequency,power,spower,formal_name)        
     plot_log_pgram(ax_logpgram,frequency,power,spower,formal_name)  
 
@@ -235,6 +235,7 @@ if __name__ == '__main__':
 
     hdul = fits.HDUList([hdu, tab])
     hdul.writeto('../data/normal/hlsp_halo_k2_llc_%s_-c%s_kepler_v1_lc.fits' % (epic,campaign),overwrite=True)
+    print('Written Halo K2SC light curve to  ../data/normal/hlsp_halo_k2_llc_%s_-c%s_kepler_v1_lc.fits' % (epic,campaign))
 
 
     if args.do_plot:

### 2019-05-16 scripts/correct_unsaturated.py
exp

@@ -239,7 +239,7 @@ if __name__ == '__main__':
 
 
     if args.do_plot:
-        plot_k2sc(lc_out,np.nanmean(tpf.flux,axis=0),weightmap.T,formal_name='(EPIC %s) Detrended' % epic,mask=tpf.pipeline_mask,
+        plot_k2sc(lc_out,np.nanmean(tpf.flux,axis=0),weightmap.T,formal_name='(EPIC %s)' % epic,mask=tpf.pipeline_mask,
             save_file='../data/normal/epic_%s.png' % (epic))
         print('Saved figure to ../data/normal/epic_%s.png' % (epic))
 

### 2019-05-16 scripts/correct_halo.py
publication figure

@@ -205,7 +205,7 @@ if __name__ == '__main__':
         dummy = fits.getheader('%s/%s' % (ddir_raw,tpf_fname)) # get the old header from the TPF
         dummy['NAXIS']=1
         dummy['halo'] =(halophot.__version__,'halophot version')
-        dummy['objective']=(objective,'halophot objective')
+        dummy['obj']=(objective,'halophot objective')
         dummy['sub']=(1,'halophot subsampling')
         dummy['starname']=(starname,'Star Identifier')
 
@@ -215,6 +215,7 @@ if __name__ == '__main__':
 
         hdul = fits.HDUList([hdu, tab])
         hdul.writeto('%s/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.fits' % (savedir,epic,campaign),overwrite=True)
+        print('Written to %s/hlsp_halo_k2_llc_%s_-c%d_kepler_v1_lc.fits' % (savedir,epic,campaign))
 
     else:
         args.do_plot = True # in case you forgot!  

### 2019-05-16 paper/ms.tex
setting the objective function is now a subsection
publication figure
planets comparison figure and text

@@
 
+%  improvements
+Unlike other methods for calibrating \kepler systematics, other than the value of $\delta$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
+The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
+It is therefore likely that significant improvements can be made to the method by including cotrending basis vectors with mean zero and whose weights are allowed to be negative, which would represent systematics which are common to all pixels in the halo aperture and therefore masquerade as signal.
+Any linear combination of convex objective functions is itself convex, and future extensions to the method could enforce combinations of different lags and orders to better represent systematics occurring on different timescales (e.g.
+thruster firings, red noise) and with different levels of smoothness.
+
+% describe changes with respect to Pleiades and Aldebaran papers: deathstar
+
+In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination.
+We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out.
+\textcolor{red}{More here from Tim.} Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion.
+We now iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
+
+% incorporation of k2sc
+While the halo procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion.
+In order to correct these, we employ the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$.
+The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction for the $x,y$ component evaluated for fixed time represents the pointing systematics.
+We subtract the systmatics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
+The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112.
+As a result \textsc{k2sc}-corrected data are not available for these targets.
+
+\subsection{Choosing the Objective Function}
+\label{sec:objective}
 % benchmarking with lags and objective functions
@@
 On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.
+
+We accordingly use a lag $\delta=10$ for all long cadence light curves, and a lag $\delta=300$ for short cadence for consistency in timescale with the long cadence processing.
 
@@
 
-%  improvements
-Unlike other methods for calibrating \kepler systematics, other than the value of $\delta$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
-The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
-It is therefore likely that significant improvements can be made to the method by including cotrending basis vectors with mean zero and whose weights are allowed to be negative, which would represent systematics which are common to all pixels in the halo aperture and therefore masquerade as signal.
-Any linear combination of convex objective functions is itself convex, and future extensions to the method could enforce combinations of different lags and orders to better represent systematics occurring on different timescales (e.g.
-thruster firings, red noise) and with different levels of smoothness.
-
-% describe changes with respect to Pleiades and Aldebaran papers: deathstar
-
-In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination.
-We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out.
-\textcolor{red}{More here from Tim.} Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion.
-We now iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
-
-% incorporation of k2sc
-While the halo procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion.
-In order to correct these, we employ the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$.
-The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction for the $x,y$ component evaluated for fixed time represents the pointing systematics.
-We subtract the systmatics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
-The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112.
-As a result \textsc{k2sc}-corrected data are not available for these targets.
-
 % figure
@@
 \begin{figure*}
-\plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.pdf}
+\plotone{rho_leo_pub.pdf}
+\label{fig:rholeo}
 \caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis.
@@
 Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}.
-The period at maximum power (16\,d) is marked on all plots, though for $\rho$~Leonis all variability is consistent with red noise (Bowman et al., 2019).}
+The period at maximum power (16\,d) is marked on all plots, though for $\rho$~Leonis all variability is consistent with red noise \citep{bowman19}.}
+\end{figure*}
+
+\subsection{Benchmarking}
+\label{sec:benchmarking}
+
+As the halo method is the only available means of obtaining light curves of stars as bright as in our sample, and they are ubiquitously found to be variable, it is difficult based on this sample alone to determine the accuracy and precision of the light curves obtained.
+While \citet{Kallinger2018} have found agreement between the \citet{White2017} halo observations of Atlas and their BRITE-Constellation observations, the BRITE observations have a lower precision and cannot be obtained for most of the stars in our sample.
+
+We want to compare the photometric precision obtained to that from SAP and normal calibration pipelines, and ascertain whether we systematically distort the scale of variation or the power spectrum of variability.
+In order to do this, we take the sample of stars with $11.5 <  Kp < 12.5$ from \ktwo Campaign~6, for which \textsc{k2sc} light curves are available, choosing~2466 stars that are as bright as possible without saturation.
+The planets in this campaign are well characterized \citep[e.g.][]{Pope2016planets}, and eight singly-transiting systems are known in this magnitude range.
+We take the entire target pixel file without using any aperture restriction, and run TV-min with $\delta = 10$ for each of these planets and compare these to light curves from the PDC pipeline.
+In both cases, we correct residual systematics with \textsc{k2sc}, prewhiten with the GP time trend model, clip $3\,\sigma$ upwards outliers, and normalize the final fluxes to unity.
+These are then folded on the known transit period and zero epoch as tabulated in the NASA Exoplanet Archive \citep{2013PASP..125..989A}, and the folded lightcurves are binned in 3-cadence bins to reduce white noise in the comparison.
+The results are displayed in Figure~\ref{fig:planets}.
+
+\begin{figure*}
+\plotone{planets_halo_pdc.pdf}
+\label{fig:planets}
+\caption{The eight transiting single-planet systems in \ktwo Campaign~6 in the magnitude range $11.5 < Kp < 12.5$, with PDC light curves (blue) and TV-min light curves (orange) overlaid.
+These have been identically \textsc{k2sc}-corrected, whitened, outlier-clipped, folded and binned as described in Section~\ref{sec:benchmarking}.
+The depths and shapes of the transits agree closely except for EPIC~212460519, for which the TV-min transit is slightly shallower, and EPIC~212555594, for which TV-min is significantly shallower.}
 \end{figure*}

### 2019-05-16 paper/ms.tex
names of red giant stars'

@@
 While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry or high-resolution spectroscopy, and they typically have long histories of previous observations.
+Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision lightcurves.
 
@@
 
+We now seek to establish the global noise properties of the whole unsaturated sample, and compare these to PDC.
+We process all~2466 stars with TV-min and $\delta = 10$, using all pixels in the TPF unmasked.
+Because these stars are so bright and the TPFs so small, in the great majority  of cases we do not expect significant contamination, and this is a way of testing how well the weights assigned by TV-min match the flux distribution over pixels.
+
 \section{Sample}
@@
 \label{sec:discussion}
-
-% how well did we do?
-\textcolor{red}{How well do we do? How do we quantify our lightcurve SNR?}
 

### 2019-05-16 paper/ms.tex
brite citations

@@
 High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models.
-This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J} and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).
+This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).
 

### 2019-05-16 paper/ms.tex
jie is coauthor

@@
 \affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0002-0007-6211]{Jie Yu}
+\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
 \affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
@@
 % do hot star asteroseismology and red giants as benchmarks, interferometry
-Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.), the Hyades giants (White et al., in prep.), and main-sequence stars (Greklek-McKeon et al., in prep.).
+Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.), interferometry of the Hyades giants (White et al., in prep.), and main-sequence stars (Greklek-McKeon et al., in prep.).
 

### 2019-05-16 paper/ms.tex
affiliations correct
mag cut figures

@@
 \affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
 \affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"{o}nigstuhl 17, D-69117 Heidelberg}
-\affiliation{Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
 
@@
 Because these stars are so bright and the TPFs so small, in the great majority  of cases we do not expect significant contamination, and this is a way of testing how well the weights assigned by TV-min match the flux distribution over pixels.
+For each lightcurve we calculate the 6.5\,hr CDPP proxy with \texttt{lightkurve} as a measure of SNR, and we plot the results of the two pipelines against one another in Figure~\ref{fig:halovspdc}.
+We see that a significant number of stars have high PDC CDPP but low TV-min CDPP, which raises the possibility that these are variables for which halo is overcorrecting.
+We find by inspection of the weightmaps and \kepler pipeline aperture masks that these mostly consist of stars for which the SAP aperture is significantly smaller than the PSF.
+In this case, by ignoring the pipeline apertures, \texttt{halophot} is in fact generating significantly better light curves.
+Over all stars, we find that the fractional enclosed halo weight in the \kepler pipeline aperture is only $0.19 \pm 0.11$, which suggests that in fact the apertures are systematically smaller than optimal for stars of this magnitude, and that TV-min is using information in the fainter pixels to help correct systematics.
+
+\begin{figure}
+\plotone{halo_pdc_comparison.png}
+\label{fig:halovspdc}
+\caption{Correlation diagram of the \texttt{lightkurve}-computed 6.5\,hr CDPP for \ktwo Campaign~6 stars in the magnitude range $11.5 < Kp < 12.5$, as processed with the PDC pipeline ($x$-axis) and TV-min pipeline ($y$-axis), both after correction and whitening with \textsc{k2sc}.
+The severe outliers where halo significantly outperforms PDC are shown by individual inspection to consist of stars for which there is contamination, or for which the SAP aperture assigned by the \kepler pipeline is significantly smaller than the PSF.}
+\end{figure}
+
+\begin{figure}
+\plotone{halo_pdc_histograms.pdf}
+\label{fig:cdpphists}
+\caption{}
+\end{figure}
 

### 2019-05-16 paper/ms.tex
new updates

@@
 \plotone{rho_leo_pub.pdf}
-\label{fig:rholeo}
 \caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis.
@@
 The period at maximum power (16\,d) is marked on all plots, though for $\rho$~Leonis all variability is consistent with red noise \citep{bowman19}.}
+\label{fig:rholeo}
 \end{figure*}
@@
 \plotone{planets_halo_pdc.pdf}
-\label{fig:planets}
 \caption{The eight transiting single-planet systems in \ktwo Campaign~6 in the magnitude range $11.5 < Kp < 12.5$, with PDC light curves (blue) and TV-min light curves (orange) overlaid.
@@
 The depths and shapes of the transits agree closely except for EPIC~212460519, for which the TV-min transit is slightly shallower, and EPIC~212555594, for which TV-min is significantly shallower.}
+\label{fig:planets}
 \end{figure*}
@@
 \plotone{halo_pdc_comparison.png}
-\label{fig:halovspdc}
 \caption{Correlation diagram of the \texttt{lightkurve}-computed 6.5\,hr CDPP for \ktwo Campaign~6 stars in the magnitude range $11.5 < Kp < 12.5$, as processed with the PDC pipeline ($x$-axis) and TV-min pipeline ($y$-axis), both after correction and whitening with \textsc{k2sc}.
 The severe outliers where halo significantly outperforms PDC are shown by individual inspection to consist of stars for which there is contamination, or for which the SAP aperture assigned by the \kepler pipeline is significantly smaller than the PSF.}
+\label{fig:halovspdc}
 \end{figure}
+
+Histograms of the CDPPs of the SAP, PDC and halo light curves with and without \textsc{k2sc} are displayed in Figure~\ref{fig:cdpphists}.
+We see that both halo and PDC significantly outperform SAP, with halo performing better than PDC with no additional correction.
+Nevertheless, after \textsc{k2sc}, we find that the best PDC lightcurves have a smaller CDPP than the best similarly pointing-corrected halo.
+We conjecture that PDC with its improved calibration for common-mode systematics and blended/background light is correcting for effects that halo, as a single-star and instrument-agnostic method, does not.
 
@@
 \plotone{halo_pdc_histograms.pdf}
+\caption{Histograms of the \texttt{lightkurve}-computed 6.5\,hr CDPP for five different pipelines applied to \ktwo Campaign~6 stars in the magnitude range $11.5 < Kp < 12.5$: SAP (purple dashed), PDC with (blue solid) and without (blue dashed) \textsc{k2sc}, and TV-min with (orange solid) and without (orange dashed) \textsc{k2sc}.}
 \label{fig:cdpphists}
-\caption{}
 \end{figure}
@@
 These can be used to constrain stellar fundamental parameters, and detailed studies of the deviations from this asymptotic limit for acoustic $p$-modes, for example due to their interaction with gravity-wave $g$-modes, can be used to accurately determine the stellar evolutionary state, for example to distinguish hydrogen shell burning red giant branch from helium core burning red clump stars.
+Summary plots for a good example of such a star, $\eta$~Cancri, are shown in Figure~\ref{fig:etacnc}.
 
@@
 This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).
+
+\begin{figure*}
+\plotone{eta_cnc_pub.pdf}
+\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the red giant $\eta$~Cancri, in the same format as Figure~\ref{fig:rholeo}.
+Solar like oscillations are clearly detected with $\numax = 22.9 \pm 0.9$ and $\Dnu = 2.7 \pm 0.03$.}
+\label{fig:etacnc}
+\end{figure*}
 

### 2019-05-16 paper/ms.tex
owl reference

@@
 This method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters, and was applied to Aldebaran with further developments by \citet{Farr2018}.
-Because SAP is not possible, we consider instead the unsaturated pixels $p_j$ at the wings of the broad and structured PSF.
+We follow the `OWL' concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions.
+We assume that a star has a wide PSF sampled by many pixels with different sensitivities, which moves around on the detector within a small region and which may vary to a small extent in time.
+We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or noise processes.
+Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general.
+
+The additional constraint beyond the OWL axioms is that some pixels are saturated, so that SAP is not possible.
+We consider instead the unsaturated pixels $p_j$ at the wings of the broad and structured PSF.
 We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux at cadence $i$ is
@@
 Unlike other methods for calibrating \kepler systematics, other than the value of $\delta$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
+The signal and the noise are jointly estimated from the data.
 The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
+
 It is therefore likely that significant improvements can be made to the method by including cotrending basis vectors with mean zero and whose weights are allowed to be negative, which would represent systematics which are common to all pixels in the halo aperture and therefore masquerade as signal.

### 2019-05-17 paper/ms.tex
bedding abstract

@@
 While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars, which saturate the detector, are important because they can be and have been observed by other instruments at very high signal-to-noise ratio.
-By considering the unsaturated scattered light `halo' around these stars we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
+By analyzing the unsaturated scattered-light `halo' around these stars, we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
 The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars.

### 2019-05-17 paper/ms.tex
bedding introduction

@@
 The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}.
-In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler the exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and these saturated stars were intentionally avoided.
+In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and intentionally avoided.
 In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars.
-While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry or high-resolution spectroscopy, and they typically have long histories of previous observations.
+While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations.
 Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision lightcurves.
@@
 % briefly intro the halo method and halo literature
-In order to recover precise photometry of the brightest stars in \ktwo, we have therefore developed two main approaches, `smear' and `halo' photometry.
+In order to recover precise light curves of the brightest stars in \ktwo, we have therefore developed two main approaches, `smear' and `halo' photometry.
 Smear photometry \citep{Pope2016} uses collateral `smear' calibration data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
-This can be processed recover light curves of stars which were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns.
+This can be processed recover light curves of stars that were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns.
 The main disadvantage of this method is that it confuses all stars in the same column, which means that in crowded fields smear light curves tend to be significantly contaminated.
@@
 The more precise method of halo photometry, which is the subject of this paper, uses the broad `halo' of scattered light around a saturated star to recover relative photometry, by constructing a light curve as a linear combination of individual pixel time series and minimizing a Total Variation objective function (TV-min).
-It has been employed for example on the Pleiades \citep{White2017} and the brightest-ever star on \kepler silicon, Aldebaran \citep{Farr2018}, recovering photometry with a precision nearly that of normally-obtained \ktwo observations of unsaturated stars.
-Unlike smear, this requires downloading data out to a 12--20~pixel radius around each star, and has accordingly only been possible for stars that were specifically targeted with apertures optimized for this method and for a small number of other stars for which this is fortuitously the case.
+It has been employed for example on the Pleiades \citep{White2017} and the brightest-ever star on \kepler silicon, Aldebaran \citep{Farr2018}, recovering photometry with a precision close to that normally obtained from \ktwo observations of unsaturated stars.
+Unlike smear, this requires downloading data out to a 12--20~pixel radius around each star, and has accordingly only been possible for stars that were specifically proposed and targeted with apertures optimized for this method, plus a small number of other stars for which this is fortuitously the case.
 The pixel requirements for this are sufficiently low that, with the help of the \ktwo Guest Observer office, such apertures were obtained for most of the bright targets from Campaign~4 onwards.
@@
 We show that the method as previously employed applying standard TV-min is suboptimal, and gain a modest improvement from taking finite differences close to the timescale of \ktwo thruster firings.
+We also document the main changes in the halo data reduction pipeline, \texttt{halophot}, with respect to previous releases.
 We go on to present complete catalog of long-cadence \ktwo halo light curves, which we have made publicly available.
 We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability.
-We also document the main changes in the halo data reduction pipeline, \texttt{halophot}, with respect to previous releases.
 These include oscillating red giants, pulsating and quiet main sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with space photometry.

### 2019-05-17 paper/ms.tex
bedding introduction

@@
 The more precise method of halo photometry, which is the subject of this paper, uses the broad `halo' of scattered light around a saturated star to recover relative photometry, by constructing a light curve as a linear combination of individual pixel time series and minimizing a Total Variation objective function (TV-min).
-It has been employed for example on the Pleiades \citep{White2017} and the brightest-ever star on \kepler silicon, Aldebaran \citep{Farr2018}, recovering photometry with a precision close to that normally obtained from \ktwo observations of unsaturated stars.
+It has been employed for example on the Pleiades \citep{White2017} and the brightest-ever star on \kepler silicon, Aldebaran \citep[$\alpha$\,Tau;][]{Farr2018}, recovering photometry with a precision close to that normally obtained from \ktwo observations of unsaturated stars.
 Unlike smear, this requires downloading data out to a 12--20~pixel radius around each star, and has accordingly only been possible for stars that were specifically proposed and targeted with apertures optimized for this method, plus a small number of other stars for which this is fortuitously the case.
@@
 We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability.
-These include oscillating red giants, pulsating and quiet main sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with space photometry.
-We hope that this diverse catalog of light curves will be useful for an equally-diverse range of astrophysical investigations.
+These include oscillating red giants, pulsating and quiet main-sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with space photometry.
+We hope that this diverse catalog of light curves will be useful for a range of astrophysical investigations.
 

### 2019-05-17 paper/ms.tex
all bedding changes made

@@
 % describe saturation
-The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}.
-For objects brighter than this, additional photons create excess electrons which `bleed' into adjacent pixels in both directions along the column containing the bright star.
-Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit of stars as bright as 16~Cyg~AB, $\theta$~Cyg and RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}.
-In the nominal \kepler mission this was not attempted for all such bright stars, and in \ktwo, the several-pixel spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.
-While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is rendered impossible for the very brightest stars whose bleed columns may run to the edge of the detector.
+The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, since these both represent sums of 6\,s exposures \citep{Gilliland2010}.
+For objects brighter than this, excess electrons `bleed' into adjacent pixels in both directions along the column containing the star.
+Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit of the $V = 6$ 16~Cyg~AB, $V=4.48$ $\theta$~Cyg, and the $V=7.2$ RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}.
+In the nominal \kepler mission this was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.
+While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is not possible for the very brightest stars whose bleed columns may run to the edge of the detector.
 Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo.
@@
 
+\newpage
+
 \section{Halo Photometry Method}
@@
 % describe halo algorithm
-This method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters, and was applied to Aldebaran with further developments by \citet{Farr2018}.
+This method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters.
+It was also applied to Aldebaran with further developments by \citet{Farr2018}.
 We follow the `OWL' concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions.
@@
 The additional constraint beyond the OWL axioms is that some pixels are saturated, so that SAP is not possible.
-We consider instead the unsaturated pixels $p_j$ at the wings of the broad and structured PSF.
+Instead the measurements are made using the unsaturated pixels $p_j$ at the wings of the broad and structured PSF.
 We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux at cadence $i$ is
@@
 \textcolor{red}{More here from Tim.} Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion.
-We now iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
+We instead chose to iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
 
 % incorporation of k2sc
-While the halo procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion.
-In order to correct these, we employ the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$.
+While the halo procedure produced a fairly clean light curve in most cases, there were nevertheless residual systematic errors related to spacecraft motion.
+In order to correct these, we employed the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$.
 The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction for the $x,y$ component evaluated for fixed time represents the pointing systematics.
-We subtract the systmatics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
+We subtracted the systmatics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
+Campaigns~9, 10, and~11 were observed in two blocks each, denoted C91/C92, C101/C102 and C111/C112 by the \ktwo Team.
 The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112.
@@
 
-In order to choose the values for $k$ and $\delta$ in our objective function, we have selected the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the sample of stars with halo apertures, and one with very little high frequency variability detected or predicted, which was also observed at short cadence.
-We choose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better.
-We calculate halo lightcurves and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data.
+In order to choose the values for $k$ and $\delta$ in our objective function, we used the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the sample of stars with halo apertures, and one with very little high frequency variability detected or predicted.
+It was also observed at short cadence.
+We chose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better.
+
+We calculated halo lightcurves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data.
 The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}.
-We find that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP.
+We found that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP.
 This is unsurprising: that this is one cadence shorter than the 12~cadence thruster firing period.
@@
 
-% figure
-
 \begin{figure*}
@@
 Because these stars are so bright and the TPFs so small, in the great majority  of cases we do not expect significant contamination, and this is a way of testing how well the weights assigned by TV-min match the flux distribution over pixels.
-For each lightcurve we calculate the 6.5\,hr CDPP proxy with \texttt{lightkurve} as a measure of SNR, and we plot the results of the two pipelines against one another in Figure~\ref{fig:halovspdc}.
+For each lightcurve we calculated the 6.5\,hr CDPP proxy with \texttt{lightkurve} as a measure of SNR, and we plot the results of the two pipelines against one another in Figure~\ref{fig:halovspdc}.
 We see that a significant number of stars have high PDC CDPP but low TV-min CDPP, which raises the possibility that these are variables for which halo is overcorrecting.
-We find by inspection of the weightmaps and \kepler pipeline aperture masks that these mostly consist of stars for which the SAP aperture is significantly smaller than the PSF.
+We found by inspection of the weightmaps and \kepler pipeline aperture masks that these mostly consist of stars for which the SAP aperture is significantly smaller than the PSF.
 In this case, by ignoring the pipeline apertures, \texttt{halophot} is in fact generating significantly better light curves.
-Over all stars, we find that the fractional enclosed halo weight in the \kepler pipeline aperture is only $0.19 \pm 0.11$, which suggests that in fact the apertures are systematically smaller than optimal for stars of this magnitude, and that TV-min is using information in the fainter pixels to help correct systematics.
+Over all stars, we found that the fractional enclosed halo weight in the \kepler pipeline aperture is only $0.19 \pm 0.11$, which suggests that in fact the apertures are systematically smaller than optimal for stars of this magnitude, and that TV-min is using information in the fainter pixels to help correct systematics.
 
@@
 We see that both halo and PDC significantly outperform SAP, with halo performing better than PDC with no additional correction.
-Nevertheless, after \textsc{k2sc}, we find that the best PDC lightcurves have a smaller CDPP than the best similarly pointing-corrected halo.
+Nevertheless, after \textsc{k2sc}, we found that the best PDC lightcurves have a smaller CDPP than the best similarly pointing-corrected halo.
 We conjecture that PDC with its improved calibration for common-mode systematics and blended/background light is correcting for effects that halo, as a single-star and instrument-agnostic method, does not.
@@
 The full sample of stars for which halo apertures were obtained is listed in Table~\ref{table_all}.
-While some very bright stars were observed with conventional apertures as part of these programs, simple aperture photometry is satisfactory on these targets and we exclude them from the present discussion and data release, which is oriented strictly towards targets only observable with halo photometry.
+Some very bright stars were observed with conventional apertures as part of these programs, but we exclude them from the present discussion and data release, which is oriented towards targets only observable with halo photometry.
 % normal apertures in 6
-We make an exception for Spica, which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture.
-In Campaign~6 it was assigned a normal aperture by mistake and simple aperture photometry performed extremely poorly, so we have processed it with the halo pipeline.
-The stars in Campaign~18 were also on-silicon in Campaign~5, but were not assigned apertures suitable for halo photometry in C5.
-A possible further extension of the present work would be to recover C5 light curves for these objects using either or both of smear or modified halo photometry.
+We include $\alpha$\,Vir (Spica), which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture.
+In Campaign~6 it was assigned a normal aperture by mistake and simple aperture photometry performed extremely poorly, so we have processed these data with the halo pipeline.
+The stars in Campaign~18 in our sample were also on-silicon in Campaign~5, but were not assigned apertures suitable for halo photometry in C5.
+A possible further extension of the present work would be to recover C5 light curves for these objects using smear and/or modified halo photometry.
 
 % short cadence availability 
-Seven stars in Campaign~13 and one in Campaign~16 were not only assigned long-cadence halo apertures, but also downloaded at short cadence.
-For these targets we have provided both long and short cadence reductions.
-Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$~cad and on choice of objective function, for consistency with long cadence we have adopted a 300~cadence lag (i.e.
+Seven stars in Campaign~13 and one in Campaign~16 were assigned short-cadence halo apertures.
+For these targets we have provided both long- and short-cadence reductions.
+Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and on choice of objective function, and for consistency with long cadence, we have adopted a 300~cadence lag (i.e.
 $30 \times$ the long cadence lag of 10) and the L1 TV objective function.
-With their long timeseries the short cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo lightcurves.
+With their many time samples, the short-cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo lightcurves.
 
@@
 
-Analyses for several of the objects here have been previously published, but we here provide the first public data releases for the Pleiades' Seven Sisters \citep{White2017}, Aldebaran \citep{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{Arentoft2019}, as well as $\rho$~Leo which was studied with halo pixels but without our objective functions \citep{Aerts2018}.
+Analyses for some of our sample have been previously published, we include their light curves in this data release: the Pleiades Seven Sisters \citep{White2017}, $\alpha$~Tau \citep[Aldebaran;][]{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{Arentoft2019}, as well as $\rho$~Leo, which was studied with halo pixels but without our objective functions \citep{Aerts2018}.
 
@@
 The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity.
-We detect variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star with a period of 1.74\,d.
-This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star imply an 0.3 \rsun companion, almost certainly of stellar mass.
+We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star with a period of 1.74\,d.
+This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.
 With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.
@@
 % do hot star asteroseismology and red giants as benchmarks, interferometry
-Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.), interferometry of the Hyades giants (White et al., in prep.), and main-sequence stars (Greklek-McKeon et al., in prep.).
+Some of the objects presented here are the subject of more detailed work in preparation, namely $\alpha$\,Vir (Spica), interferometry of the Hyades giants, and main-sequence stars.
 
 % do k2 smear after that
-The sample of K2 bright stars presented here only includes those with halo apertures, but while some others are available conventionally, many were not assigned target pixels and were not downloaded at all.
-Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., under review), and this can also be done in K2, although in the latter case the sample is much smaller due to competition with halo apertures and the systematics correction is more challenging.
+The sample of K2 bright stars presented here only includes those with halo apertures.
+While some others are available conventionally, many were not assigned target pixels and were not downloaded at all.
+Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., under review), and this can also be done in K2, although the sample is much smaller due to allocation of halo apertures and the systematics correction is more challenging.
 A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.
@@
 The halo method naturally extends to other contexts where simple aperture photometry is not possible, such as for saturated stars observed by the Transiting Exoplanet Survey Satellite \citep[TESS;][]{tess}.
-Although the saturation limit is brighter ($T_{mag} \sim 6$) and this problem accordingly affects fewer stars and less badly, there are situations such as for $\alpha$~Centauri or $\beta$~Hydri where the bleed column reaches the edge of the chip and a SAP light curve is irrecoverable.
-We expect that TV-min halo photometry will therefore be valuable in ensuring that TESS can observe even the very brightest stars.
+Although the saturation limit is brighter ($T_{mag} \sim 6$) and this problem accordingly affects fewer stars and less badly, there are stars such as $\alpha$~Centauri and $\beta$~Hydri where the bleed column reaches the edge of the chip and a SAP light curve is irrecoverable.
+We expect that TV-min halo photometry will therefore be valuable in ensuring that TESS can observe the very brightest stars.
+
+% halo method
 

### 2019-05-17 paper/ms.tex
last paragraphs

@@
 % halo method
+There are directions for improvement of the halo method itself, and for applying it beyond \kepler/\ktwo and TESS.
+It remains to be seen how well the method of optimizing convex objective functions can deal with significantly varying PSFs, such as from ground-based observations.
+The rapidly varying and moving seeing-limited PSF couples to flat field errors as is the case with \kepler, and leads to severe short-timescale instrumental noise.
+Self-calibration by the halo method, or a similar method, may permit improvements in ground-based photometry.
+Likewise, there may be other convex objective functions, including linear combinations of currently-used objective functions, which offer superior performance, for example by using combinations of different lagged functions to suppress systematics occurring at different timescales.
+The remaining unexplored space of convex objective functions suitable may offer significant improvements on existing self-calibration techniques in high-cadence photometry and related problems in astronomy.
 

### 2019-05-17 paper/ms.tex
lagged for Will

@@
 The key methodology is to optimize the weights of a linear combination of pixel time series with respect to an objective function.
-We test a range of such objective functions, finding that generalizations of Total Variation perform well on both saturated and unsaturated \ktwo targets.
+We test a range of such objective functions, finding that \textit{lagged Total Variation}, a generalization of Total Variation, performs well on both saturated and unsaturated \ktwo targets.
 Applying this to the bright stars across the \ktwo Campaigns, this reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.

### 2019-05-21 paper/ms.tex
proper names are resolved as normal designations

@@
 High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models.
-This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).
+This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, accepted ApJS).
 
@@
 While some others are available conventionally, many were not assigned target pixels and were not downloaded at all.
-Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., under review), and this can also be done in K2, although the sample is much smaller due to allocation of halo apertures and the systematics correction is more challenging.
+Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., 2019, accepted ApJS), and this can also be done in K2, although the sample is much smaller due to allocation of halo apertures and the systematics correction is more challenging.
 A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.

### 2019-05-28 paper/ms.tex
dois and links

--- 2019-05-17 paper/ms.tex
@@
 In order to recover precise light curves of the brightest stars in \ktwo, we have therefore developed two main approaches, `smear' and `halo' photometry.
-Smear photometry \citep{Pope2016} uses collateral `smear' calibration data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
+Smear photometry \citep{Pope2016,smearcampaign} uses collateral `smear' calibration data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
 This can be processed recover light curves of stars that were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns.
@@
 High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models.
-This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).
+This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.
 
@@
 
+\section{Data Release and Open Science}
+
+The software \texttt{halophot} that implements halo photometry as described in this paper is available under a GPLv3 license from \href{https://github.com/hvidy/halophot}{github.com/hvidy/halophot}.
+
+All light curves presented in this paper are available as High-Level Science Products from the Mikulski Archive for Space Telescopes\footnote{\dataset[10.17909/t9-6wj4-eb32]{\doi{10.17909/t9-6wj4-eb32}}}.
+They are also available, together with the source code that produced the survey sample and this manuscript, from \href{https://github.com/benjaminpope/k2halo}{github.com/benjaminpope/k2halo}.
+
 \section{Conclusions}
@@
 While some others are available conventionally, many were not assigned target pixels and were not downloaded at all.
-Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., under review), and this can also be done in K2, although the sample is much smaller due to allocation of halo apertures and the systematics correction is more challenging.
+Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler \citep{smearcampaign}, and this can also be done in K2, although the sample is much smaller due to allocation of halo apertures and the systematics correction is more challenging.
 A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.
@@
 
-\software{IPython  \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}
+\software{\textsc{k2sc} \citep{Aigrain2015,k2sc}; IPython  \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}
 

### 2019-05-31 paper/ms.tex
guniibuu is 36 oph in gamilaraay

@@
 While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations.
-Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision lightcurves.
+Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision light curves.
 
@@
 Smear photometry \citep{Pope2016,smearcampaign} uses collateral `smear' calibration data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD.
-This can be processed recover light curves of stars that were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns.
+This can be processed to recover light curves of stars that were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns.
 The main disadvantage of this method is that it confuses all stars in the same column, which means that in crowded fields smear light curves tend to be significantly contaminated.
@@
 We also document the main changes in the halo data reduction pipeline, \texttt{halophot}, with respect to previous releases.
-We go on to present complete catalog of long-cadence \ktwo halo light curves, which we have made publicly available.
+We go on to present a complete catalog of long-cadence \ktwo halo light curves, which we have made publicly available.
 We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability.
-These include oscillating red giants, pulsating and quiet main-sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with space photometry.
-We hope that this diverse catalog of light curves will be useful for a range of astrophysical investigations.
+These include oscillating red giants, pulsating and quiet main-sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with high-cadence space photometry.
+We are convinced that this diverse catalog of high-precision light curves will be useful for a range of astrophysical investigations.
 
@@
 $Q_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
-In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.
+In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j)$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.
 
@@
 
-In order to choose the values for $k$ and $\delta$ in our objective function, we used the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the sample of stars with halo apertures, and one with very little high frequency variability detected or predicted.
+In order to choose the values for $k$ and $\delta$ in our objective function, we used the quiet system 36~Ophiuchi (Guniibuu, $V= 5.08$), a K1/K2/K5 main sequence triple system consisting of the lowest-mass main sequence stars in the sample of stars with halo apertures.
+Very little high frequency variability is detected or predicted.
 It was also observed at short cadence.
-We chose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better.
+We chose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a light curve, with lower being better.
 
-We calculated halo lightcurves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data.
+We calculated halo light curves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data.
 The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}.
@@
 In both cases, we correct residual systematics with \textsc{k2sc}, prewhiten with the GP time trend model, clip $3\,\sigma$ upwards outliers, and normalize the final fluxes to unity.
-These are then folded on the known transit period and zero epoch as tabulated in the NASA Exoplanet Archive \citep{2013PASP..125..989A}, and the folded lightcurves are binned in 3-cadence bins to reduce white noise in the comparison.
+These are then folded on the known transit period and zero epoch as tabulated in the NASA Exoplanet Archive \citep{2013PASP..125..989A}, and the folded light curves are binned in 3-cadence bins to reduce white noise in the comparison.
 The results are displayed in Figure~\ref{fig:planets}.
@@
 Because these stars are so bright and the TPFs so small, in the great majority  of cases we do not expect significant contamination, and this is a way of testing how well the weights assigned by TV-min match the flux distribution over pixels.
-For each lightcurve we calculated the 6.5\,hr CDPP proxy with \texttt{lightkurve} as a measure of SNR, and we plot the results of the two pipelines against one another in Figure~\ref{fig:halovspdc}.
+For each light curve we calculated the 6.5\,hr CDPP proxy with \texttt{lightkurve} as a measure of SNR, and we plot the results of the two pipelines against one another in Figure~\ref{fig:halovspdc}.
 We see that a significant number of stars have high PDC CDPP but low TV-min CDPP, which raises the possibility that these are variables for which halo is overcorrecting.
@@
 We see that both halo and PDC significantly outperform SAP, with halo performing better than PDC with no additional correction.
-Nevertheless, after \textsc{k2sc}, we found that the best PDC lightcurves have a smaller CDPP than the best similarly pointing-corrected halo.
+Nevertheless, after \textsc{k2sc}, we found that the best PDC light curves have a smaller CDPP than the best similarly pointing-corrected halo.
 We conjecture that PDC with its improved calibration for common-mode systematics and blended/background light is correcting for effects that halo, as a single-star and instrument-agnostic method, does not.
@@
 $30 \times$ the long cadence lag of 10) and the L1 TV objective function.
-With their many time samples, the short-cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo lightcurves.
+With their many time samples, the short-cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo light curves.
 

### 2019-05-31 paper/ms.tex
misc

@@
 
+\author[0000-0003-1540-8562]{Will M. Farr}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
+\affiliation{Department of Physics and Astronomy, Stony Brook University, Stony Brook, NY 11794, USA}
+
+\author[0000-0002-0007-6211]{Jie Yu}
+\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+
 \author[0000-0003-1822-7126]{Conny Aerts}
@@
 
-\author[0000-0003-1540-8562]{Will M. Farr}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
-\affiliation{Department of Physics and Astronomy, Stony Brook University, Stony Brook, NY 11794, USA}
-
 \author[0000-0003-2866-9403]{David W. Hogg}
@@
 \affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
-\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
-
-\author[0000-0002-0007-6211]{Jie Yu}
-\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
 \affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
@@
 For objects brighter than this, excess electrons `bleed' into adjacent pixels in both directions along the column containing the star.
-Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit of the $V = 6$ 16~Cyg~AB, $V=4.48$ $\theta$~Cyg, and the $V=7.2$ RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}.
+Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit t, for various types of variables.
+Examples treated in the nominal {\it Kepler\/} mission are the prototype classical radial pulsator RR\,Lyr \citep[$V=7.2$;][]{Kolenberg2011}, the solar-like pulsators 16\,Cyg\,AB \citep[$V\approx 6$;][]{2013MNRAS.433.1262W} and $\theta\,$Cyg \citep[$V=4.48$;][]{Guzik2016}, and the massive eclipsing binary V380\,Cyg \citep[$V=5.68$;][]{tkachenko2014}.
+
+of the $V = 6$ 16~Cyg~AB, $V=4.48$ $\theta$~Cyg, and the $V=7.2$ RR~Lyr \citep[e.g.][]{,}.
 In the nominal \kepler mission this was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.
@@
 For these targets we have provided both long- and short-cadence reductions.
-Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and on choice of objective function, and for consistency with long cadence, we have adopted a 300~cadence lag (i.e.
+Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and to $k \in {1,2}$, and for consistency with long cadence, we have adopted a 300~cadence lag (i.e.
 $30 \times$ the long cadence lag of 10) and the L1 TV objective function.
@@
 \caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the red giant $\eta$~Cancri, in the same format as Figure~\ref{fig:rholeo}.
-Solar like oscillations are clearly detected with $\numax = 22.9 \pm 0.9$ and $\Dnu = 2.7 \pm 0.03$.}
+Solar like oscillations are clearly detected with $\numax = 22.9 \pm 0.9$\,\muHz and $\Dnu = 2.7 \pm 0.03$\,\muHz.}
 \label{fig:etacnc}
@@
 % RGs, Classical pulsators 
-\subsection{Classical Variables}
+\subsection{Pulsators with Self-Driven Modes}
 \label{sec:variables}
@@
 The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity.
-We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star with a period of 1.74\,d.
+We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star.
 This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.
@@
 % do hot star asteroseismology and red giants as benchmarks, interferometry
-Some of the objects presented here are the subject of more detailed work in preparation, namely $\alpha$\,Vir (Spica), interferometry of the Hyades giants, and main-sequence stars.
+Some of the objects presented here are the subject of more detailed work in preparation, namely $\alpha$\,Vir (Spica), interferometry of the Hyades giants, and main-sequence stars with self-driven nonradial modes.
 

### 2019-05-31 paper/ms.tex
greklek-mckeon on paper
36 oph is active

@@
 
+\author[0000-0002-0371-1647]{Michael Greklek-McKeon}
+\affiliation{Institute for Astronomy, University of Hawai\okina i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
+
+\author[0000-0001-8832-4488 ]{Daniel Huber}
+\affiliation{Institute for Astronomy, University of Hawai\okina i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
+\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+
 \author[0000-0003-1822-7126]{Conny Aerts}
@@
 \affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"{o}nigstuhl 17, D-69117 Heidelberg}
-
-\author[0000-0001-8832-4488 ]{Daniel Huber}
-\affiliation{Institute for Astronomy, University of Hawai\okina i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
-\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
-\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
 
@@
 
-In order to choose the values for $k$ and $\delta$ in our objective function, we used the quiet system 36~Ophiuchi (Guniibuu, $V= 5.08$), a K1/K2/K5 main sequence triple system consisting of the lowest-mass main sequence stars in the sample of stars with halo apertures.
+In order to choose the values for $k$ and $\delta$ in our objective function, we used the system 36~Ophiuchi (Guniibuu, $V= 5.08$), a K1/K2/K5 active main sequence triple system consisting of the lowest-mass main sequence stars in the sample of stars with halo apertures.
 Very little high frequency variability is detected or predicted.

### 2019-05-31 paper/ms.tex
aerts edits

@@
 In the asymptotic limit, these consist of a comb of modes separated by the large frequency separation \Dnu, approximately the sound-crossing-time of the star, with a Gaussian envelope centred on the frequency of maximum power \numax, which scales with the acoustic cutoff frequency at the star's surface.
-These can be used to constrain stellar fundamental parameters, and detailed studies of the deviations from this asymptotic limit for acoustic $p$-modes, for example due to their interaction with gravity-wave $g$-modes, can be used to accurately determine the stellar evolutionary state, for example to distinguish hydrogen shell burning red giant branch from helium core burning red clump stars.
+These \Dnu and \numax values can be used to constrain stellar fundamental parameters, such as radius, mass, and age \citep[e.g.][, for a recent review]{2017A&ARv..25....1H}.
+Detailed studies of the deviations from the asymptotic limit for p-modes, e.g.
+due to acoustic glitches, provide information on the He content and mixing processes at the bottom of the convective envelope \citep[e.g.
+][]{Verma2019}.
+On the other hand, dipole mixed modes, which have a g-mode character in the inner regions of the star, fulfil an asymptotic period spacing determined by the buoyancy frequency inside the star.
+This spacing can be used to accurately determine the stellar evolutionary state and allow to distinguish between hydrogen shell and core helium burning \citep{bedding2011}.
 Summary plots for a good example of such a star, $\eta$~Cancri, are shown in Figure~\ref{fig:etacnc}.

### 2019-05-31 paper/ms.tex
no newpage
huber edits

@@
 
-\title{The K2 Bright Star Survey}
+\title{The K2 Bright Star Survey I: Methodology and Data Release}
 
@@
 \affiliation{Institute for Astronomy, University of Hawai\okina i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
-\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
-\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
 
@@
 % intro kepler
-The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}.
+The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F,2015ApJ...809....8B}.
 In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and intentionally avoided.
-In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars.
+In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars \citep{2014PASP..126..398H}.
 While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations.
@@
 We are convinced that this diverse catalog of high-precision light curves will be useful for a range of astrophysical investigations.
-
-\newpage
 
@@
 The full sample of stars for which halo apertures were obtained is listed in Table~\ref{table_all}.
+Following the successful pilot observations of the Pleiades B~stars in Campaign~4, we proposed halo photometry through dedicated K2 Guest Observer Programs from Campaign 5 onwards.
+Target selection was performed by cross-matching Hipparcos \citep{leeuwen07} with the K2 Ecliptic Plane Input Catalog \citep[EPIC,][]{huber16} and selecting all targets on silicon brighter than $Kp < 6$ on silicon.
+M giants which pulsate with periods that are too long to be resolved within a K2 campaign were removed.
+We requested short-cadence observations for a small number of unevolved stars for which the expected timescales of solar-like oscillations cannot be sufficiently sampled with long-cadence data.
+
  Some very bright stars were observed with conventional apertures as part of these programs, but we exclude them from the present discussion and data release, which is oriented towards targets only observable with halo photometry.
@@
 We include $\alpha$\,Vir (Spica), which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture.
-In Campaign~6 it was assigned a normal aperture by mistake and simple aperture photometry performed extremely poorly, so we have processed these data with the halo pipeline.
+In Campaign~6 it was assigned a normal aperture due an erroneous estimate of its \kepler magnitude and simple aperture photometry performed extremely poorly, so we have processed these data with the halo pipeline.
 The stars in Campaign~18 in our sample were also on-silicon in Campaign~5, but were not assigned apertures suitable for halo photometry in C5.
@@
 \label{sec:variables}
-\textcolor{red}{Variability catalog?}
+
+Our dataset includes a rich variety of classical pulsators.
+We used visual inspection of the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes such as $\delta$ Scuti stars, $\gamma$ Doradus stars, slowly pulsating B~stars, $\beta$ Cephei pulsators, as well as supergiants showing stochastic variability \citep[][]{Aerts2018,bowman19}.
+The classes we have determined for each star are listed in Table~\ref{table_all}.
+A detailed frequency analysis of the variability in each star will be presented in a forthcoming paper (Greklek-McKeon et al., in prep).
 
@@
 The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a Director's Discretionary Time program in Campaign 4 as GO4901.
-We are grateful for the associated funding provided by the K2 GO office which has been essential in bringing this project to fruition.
+We gratefully acknowledge financial support by the National Aeronautics and Space Administration through K2 Guest Observer Programs NNX17AF76G, 80NSSC18K0362, and 80NSSC19K0108, which has been essential in bringing this project to fruition.
 

### 2019-06-21 paper/ms.tex
aerts section

@@
 
+\subsection{Comparison with `Raw' Halo}
+\label{raw}
+
+The blue supergiant $\rho$~Leonis, observed in Campaign~14, was studied with halo photometry but without the TV-min method by \citet{Aerts2018}.
+In that reduction, \citet{Aerts2018} used four different aperture masks to extract raw light curves, and detrended these for K2 systematics with \textsc{k2sc} and a polynomial to account for long-term drift.
+They detected photometric variability at the star's rotation period of 26.8~d and also multiperiodic low-frequency variability ($<1.5 \text{d}^{-1}$).
+There is excellent agreement between the light curves produced by both methods.
+It is easiest to compare the methods in the power-spectral domain, where we see a reduction of only a few percent in the amplitude of oscillations in the TV-min and the \citet{Aerts2018} lightcurve; at high frequencies, both methods show significant residual systematics at the K2~thruster-firing frequencies, but the TV-min lightcurve shows a lower white noise floor by a factor of $\sim 3$.
+
+\begin{figure}
+\plotone{rholeo_comparison.pdf}
+\caption{Top: halo light curves of $\rho$~Leonis from \citet{Aerts2018} (blue) and TV-min from the present paper (green).
+Bottom: Lomb-Scargle power spectral densities of the Aerts (blue) and TV-min (green) observations, with smoothed power spectral densities overplotted in orange and purple respectively and the K2 thruster firing frequencies highlighted with pale blue vertical lines.
+There is excellent agreement between the light curves and power spectra at high frequencies, with some residual thruster firing systematics in both light curves, and a factor of $\sim 3$ lower white noise floor in the TV-min power spectrum.}
+\label{rholeo_comparison}
+\end{figure}
+
 \subsection{Oscillating Red Giants}

### 2019-06-21 scripts/correct_unsaturated.py

@@ -224,8 +224,11 @@ if __name__ == '__main__':
 
     dummy = fits.getheader('../data/normal/ktwo%s-c06_lpd-targ.fits.gz' % (epic)) # get the old header from the TPF
     dummy['NAXIS']=1
+    dummy['ORIGIN']=('Pope/NYU','institution responsible for creating this file ')
+    dummy['CREATOR'] = ('halophot + k2halo/scripts/correct_unsaturated.py', 'pipeline')
+
     dummy['halo'] =(halophot.__version__,'halophot version')
-    dummy['objective']=('tv','halophot objective')
+    dummy['obj']=('tv','halophot objective')
     dummy['sub']=(1,'halophot subsampling')
     dummy['starname']=(epic,'Star Identifier')
 

### 2019-06-26 paper/ms.tex
bedding edits

@@
 \begin{abstract}
-While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars, which saturate the detector, are important because they can be and have been observed by other instruments at very high signal-to-noise ratio.
+While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars that saturated the detector are important because they can be and have been observed very accurately by other instruments.
 By analyzing the unsaturated scattered-light `halo' around these stars, we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
@@
 We test a range of such objective functions, finding that \textit{lagged Total Variation}, a generalization of Total Variation, performs well on both saturated and unsaturated \ktwo targets.
-Applying this to the bright stars across the \ktwo Campaigns, this reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
-Here we describe our pipeline, and present a catalogue of the bright stars studied, with classifications and parametrizations of their variability and remarks on interesting objects.
+Applying this to the bright stars across the \ktwo Campaigns reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
+We describe our pipeline and present a catalogue of the \textcolor{red}{N} bright stars, with classifications and parametrizations of their variability and remarks on interesting objects.
 These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST).
@@
 % intro kepler
-The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F,2015ApJ...809....8B}.
+The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}.
 In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and intentionally avoided.

### 2019-07-01 paper/ms.tex
mike updates

@@
 By analyzing the unsaturated scattered-light `halo' around these stars, we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
-The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars.
+The halo method does not depend on the detailed cause and form of systematics, and we show that it is effective at extracting light curves from both normal and saturated stars.
 The key methodology is to optimize the weights of a linear combination of pixel time series with respect to an objective function.
@@
 Applying this to the bright stars across the \ktwo Campaigns reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
-We describe our pipeline and present a catalogue of the \textcolor{red}{N} bright stars, with classifications and parametrizations of their variability and remarks on interesting objects.
+We describe our pipeline and present a catalogue of the 161 bright stars, with classifications of their variability, asterosesmic parameters for giants with well-measured solar-like oscillations, and remarks on interesting objects.
 These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST).
@@
 
-Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for all 31 giants for which oscillations are detected.
-These parameters are listed in Table~\ref{rgs}.
+Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for the~31 giants for which oscillations are detected with sufficient signal-to-noise.
+These parameters are listed in Table~\ref{rgs}; the stars are noted as showing `RG' variability in Table~\ref{table_all}, whereas this field is left blank for stars of luminosity class III for which oscillations are not unambiguously detected.
 High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models.
@@
 
+\subsection{Eclipsing Binaries}
+\label{sec:ebs}
+
+We have detected two eclipsing binaries in our sample: the previously-known EB HR\,6773 and the new detection 98\,Tau.
+
+%  HR 6773  is an SPB EB
+
+% interesting EB - 98 Tau
+The chemically-peculiar A0V star 98\,Tau is of special interest for studies of surface inhomogeneity.
+We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star.
+This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.
+With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.
+
 % RGs, Classical pulsators 
-\subsection{Pulsators with Self-Driven Modes}
+\subsection{Other Variables}
 \label{sec:variables}
@@
 Our dataset includes a rich variety of classical pulsators.
-We used visual inspection of the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes such as $\delta$ Scuti stars, $\gamma$ Doradus stars, slowly pulsating B~stars, $\beta$ Cephei pulsators, as well as supergiants showing stochastic variability \citep[][]{Aerts2018,bowman19}.
+We used visual inspection of the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes.
+We identify 23 stars showing $\delta$ Scuti pulsations and 20 with $\gamma$ Doradus pulsations, including 9~with hybrid $\delta$\,Sct/$\gamma$\,Dor variability; 14~slowly pulsating B~stars (SPB stars), 3~$\beta$ Cephei pulsators, 3~Cepheids, as well as 3~O\,stars 5~supergiants showing variability \citep[as in][]{Aerts2018,bowman19}.
+In addition to this, eight stars rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn spot modulation.
 The classes we have determined for each star are listed in Table~\ref{table_all}.
-A detailed frequency analysis of the variability in each star will be presented in a forthcoming paper (Greklek-McKeon et al., in prep).
-
-\subsection{Chemically-Peculiar Stars}
-
-% interesting EB - 98 Tau
-The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity.
-We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star.
-This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.
-With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.
+A detailed frequency analysis of the variability in each star will be presented in a forthcoming paper.
 

### 2019-07-03 paper/ms.tex
cheops
deathstar section filled in

@@
 In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination.
-We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out.
-\textcolor{red}{More here from Tim.} Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion.
+Clusters of pixels are identified with the DBSCAN algorithm \citep[Density-based spatial clustering of applications with noise;][]{dbscan}, and we join these clusters with the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2}.
+Clusters other than the target star identified by this algorithm are identified as possible background sources and removed from the target pixel file before processing.
+Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion.
 We instead chose to iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
@@
 
-We have detected two eclipsing binaries in our sample: the previously-known EB HR\,6773 and the new detection 98\,Tau.
+We have detected two eclipsing binaries in our sample: the previously-known EB HR~6773 and the new detection 98~Tau.
+After subtracting an EB model for HR~6773, we find additional variability consistent with SPB pulsations.
 
@@
 % interesting EB - 98 Tau
-The chemically-peculiar A0V star 98\,Tau is of special interest for studies of surface inhomogeneity.
+The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity.
 We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star.
 This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.
-With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.
+
+These systems contain variable stars in the brightest EBs in \ktwo, and are therefore unique targets for follow-up with smaller telescopes.
+With an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} has been shown to robustly and uniquely infer surface brightness maps from light curves.
+High-time-cadence photometry during transit, such as with CHEOPS \citep{cheops}, will reveal the spatial distribution of the star's chemical peculiarity or pulsation.
 

### 2019-07-03 paper/ms.tex
capitalize dbscan

@@
 In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination.
-Clusters of pixels are identified with the DBSCAN algorithm \citep[Density-based spatial clustering of applications with noise;][]{dbscan}, and we join these clusters with the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2}.
+Clusters of pixels are identified with the DBSCAN algorithm \citep[Density-Based Spatial Clustering of Applications with Noise;][]{dbscan}, and we join these clusters with the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2}.
 Clusters other than the target star identified by this algorithm are identified as possible background sources and removed from the target pixel file before processing.

### 2019-07-03 paper/ms.tex
textsc dbscan

@@
 In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination.
-Clusters of pixels are identified with the DBSCAN algorithm \citep[Density-Based Spatial Clustering of Applications with Noise;][]{dbscan}, and we join these clusters with the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2}.
+Clusters of pixels are identified with the \textsc{dbscan} algorithm \citep[Density-Based Spatial Clustering of Applications with Noise;][]{dbscan}, and we join these clusters with the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2}.
 Clusters other than the target star identified by this algorithm are identified as possible background sources and removed from the target pixel file before processing.

### 2019-07-03 paper/ms.tex
98 Tau updates

@@
 
+\begin{figure*}
+\plotone{98_Tau_pub.pdf}
+\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the eclipsing binary 98~Tauri, in a similar format to Figure~\ref{fig:rholeo}.
+The residuals to the position and time GP are not shown, as the time GP fits poorly to the deep eclipse.
+The polynomial trend and Lomb-Scargle periodograms are conditioned on the out-of-transit points only.}
+\label{fig:98tau}
+\end{figure*}
+
 % RGs, Classical pulsators 

### 2019-07-03 paper/ms.tex
98 tau section

@@
 
-%  HR 6773  is an SPB EB
-
 % interesting EB - 98 Tau
@@
 This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.
+There are an unusually high number of background stars in the same photometric aperture as 98~Tau, and these were not all detected by \texttt{deathstar} and significantly contaminated the resulting lightcurve.
+As a result it was necessary to manually flag these objects using the `interact' mode of \texttt{lightkurve}, as displayed in Figure~\ref{fig:98tau}.
+The eclipse is deep enough to be seen by eye in the diffuse light of 98~Tau using this interactive display, and is not associated with any of the background stars.
 

### 2019-07-03 paper/ms.tex
proofread

@@
 While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars that saturated the detector are important because they can be and have been observed very accurately by other instruments.
-By analyzing the unsaturated scattered-light `halo' around these stars, we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
+By analyzing the unsaturated scattered-light `halo' around these stars, we have retrieved precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards.
 The halo method does not depend on the detailed cause and form of systematics, and we show that it is effective at extracting light curves from both normal and saturated stars.
@@
 In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars \citep{2014PASP..126..398H}.
-While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations.
+While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations.
 Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision light curves.
@@
 For objects brighter than this, excess electrons `bleed' into adjacent pixels in both directions along the column containing the star.
-Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit t, for various types of variables.
+Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit.
 Examples treated in the nominal {\it Kepler\/} mission are the prototype classical radial pulsator RR\,Lyr \citep[$V=7.2$;][]{Kolenberg2011}, the solar-like pulsators 16\,Cyg\,AB \citep[$V\approx 6$;][]{2013MNRAS.433.1262W} and $\theta\,$Cyg \citep[$V=4.48$;][]{Guzik2016}, and the massive eclipsing binary V380\,Cyg \citep[$V=5.68$;][]{tkachenko2014}.
-
-of the $V = 6$ 16~Cyg~AB, $V=4.48$ $\theta$~Cyg, and the $V=7.2$ RR~Lyr \citep[e.g.][]{,}.
-In the nominal \kepler mission this was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.
+In the nominal \kepler mission SAP was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.
 While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is not possible for the very brightest stars whose bleed columns may run to the edge of the detector.
@@
 % describe halo algorithm
-This method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters.
+The `TV-min' halo method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters.
 It was also applied to Aldebaran with further developments by \citet{Farr2018}.
@@
 We assume that a star has a wide PSF sampled by many pixels with different sensitivities, which moves around on the detector within a small region and which may vary to a small extent in time.
-We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or noise processes.
+We assume that our time series consists of many epochs sampled with a nearly even cadence.
+We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or other noise processes.
 Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general.
@@
 Instead the measurements are made using the unsaturated pixels $p_j$ at the wings of the broad and structured PSF.
-We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux at cadence $i$ is
+We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux at epoch $i$ is
 
@@
 The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse.
-The lag parameter $\delta$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below.
+The lag parameter $\delta$ allows for flexibility in modelling systematics occurring at different timescales from epoch-to-epoch, and we investigate its effects below.
 The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise.
 For convenience in the rest of this paper, we will refer to the $k=1$ case as TV, the $k=2$ case as L2V, and the $k=3$ case as L3V.
+
+\citet{parker} in their work on the saturated \ktwo observations of Titan optimized an objective function equivalent to $Q_{2,1}$ with a \emph{second}-order finite difference $2f_i -f_{i-1} -f_{i+1}$, noting that first-order differences are sensitive to linear trends while second-order differences are invariant.
+We nevertheless choose to use a first-order finite difference, on the grounds that long-term astrophysical trends on the timescale of a \ktwo Campaign cannot be straightforwardly distinguished from systematics, and that the short-timescale noise performance of optimizing $Q_{2,1}$ with respect to first-order differences was superior in our numerical experiments.
 
@@
 It is therefore likely that significant improvements can be made to the method by including cotrending basis vectors with mean zero and whose weights are allowed to be negative, which would represent systematics which are common to all pixels in the halo aperture and therefore masquerade as signal.
-Any linear combination of convex objective functions is itself convex, and future extensions to the method could enforce combinations of different lags and orders to better represent systematics occurring on different timescales (e.g.
+Any linear combination of convex objective functions is itself convex, and future extensions to the method could apply combinations of different lags and orders to better represent systematics occurring on different timescales (e.g.
 thruster firings, red noise) and with different levels of smoothness.
@@
 Clusters other than the target star identified by this algorithm are identified as possible background sources and removed from the target pixel file before processing.
-Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion.
-We instead chose to iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
+Other than this, we have adopted less-aggressive quality flagging, having found that many epochs were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion.
+We instead chose to iteratively sigma-clip outliers and use the \texttt{lightkurve} \citep{lightkurve} default quality mask.
 
@@
 The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112.
-As a result \textsc{k2sc}-corrected data are not available for these targets.
+As a result \textsc{k2sc}-corrected data are not available for these targets, and no halo light curves at all are available in C112.
 
@@
 It was also observed at short cadence.
-We chose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a light curve, with lower being better.
+We chose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} as a proxy for the `noise' in a light curve, with lower being better.
 
@@
 Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}.
-The period at maximum power (16\,d) is marked on all plots, though for $\rho$~Leonis all variability is consistent with red noise \citep{bowman19}.}
+The period at maximum power (16\,d) is marked on all plots of this form, though for $\rho$~Leonis all variability is consistent with red noise \citep{Aerts2018,bowman19}.}
 \label{fig:rholeo}
@@
 In both cases, we correct residual systematics with \textsc{k2sc}, prewhiten with the GP time trend model, clip $3\,\sigma$ upwards outliers, and normalize the final fluxes to unity.
-These are then folded on the known transit period and zero epoch as tabulated in the NASA Exoplanet Archive \citep{2013PASP..125..989A}, and the folded light curves are binned in 3-cadence bins to reduce white noise in the comparison.
+These are then folded on the known transit period and zero epoch as tabulated in the NASA Exoplanet Archive \citep{2013PASP..125..989A}, and the folded light curves are binned in 3-epoch bins to reduce white noise in the comparison.
 The results are displayed in Figure~\ref{fig:planets}.
@@
 Target selection was performed by cross-matching Hipparcos \citep{leeuwen07} with the K2 Ecliptic Plane Input Catalog \citep[EPIC,][]{huber16} and selecting all targets on silicon brighter than $Kp < 6$ on silicon.
-M giants which pulsate with periods that are too long to be resolved within a K2 campaign were removed.
+M~giants which pulsate with periods that are long compared to a K2 campaign were removed.
 We requested short-cadence observations for a small number of unevolved stars for which the expected timescales of solar-like oscillations cannot be sufficiently sampled with long-cadence data.
@@
 For these targets we have provided both long- and short-cadence reductions.
-Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and to $k \in {1,2}$, and for consistency with long cadence, we have adopted a 300~cadence lag (i.e.
-$30 \times$ the long cadence lag of 10) and the L1 TV objective function.
+Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and to $k \in {1,2}$, and for consistency with long cadence, we have adopted a 300~epoch lag (i.e.
+$30 \times$ the long-cadence lag of 10) and the L1 TV objective function.
 With their many time samples, the short-cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo light curves.
@@
 \label{sec:rgs}
-31 of the evolved stars in our sample have detectable stochastically-excited solar-like acoustic oscillations.
+31 of the evolved stars in our sample have detectable stochastically-excited solar-like acoustic (p-mode) oscillations.
 In the asymptotic limit, these consist of a comb of modes separated by the large frequency separation \Dnu, approximately the sound-crossing-time of the star, with a Gaussian envelope centred on the frequency of maximum power \numax, which scales with the acoustic cutoff frequency at the star's surface.
-These \Dnu and \numax values can be used to constrain stellar fundamental parameters, such as radius, mass, and age \citep[e.g.][, for a recent review]{2017A&ARv..25....1H}.
+These \Dnu and \numax values can be used to constrain stellar fundamental parameters, such as radius, mass, and age \citep[e.g.][for a recent review]{2017A&ARv..25....1H}.
 Detailed studies of the deviations from the asymptotic limit for p-modes, e.g.
-due to acoustic glitches, provide information on the He content and mixing processes at the bottom of the convective envelope \citep[e.g.
+due to acoustic `glitches', provide information on the He content and mixing processes at the bottom of the convective envelope \citep[e.g.
 ][]{Verma2019}.
@@
 
-Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for the~31 giants for which oscillations are detected with sufficient signal-to-noise.
+Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citet{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for the~31 giants for which oscillations are detected with sufficient signal-to-noise.
 These parameters are listed in Table~\ref{rgs}; the stars are noted as showing `RG' variability in Table~\ref{table_all}, whereas this field is left blank for stars of luminosity class III for which oscillations are not unambiguously detected.
 High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models.
-This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.
+This sample will be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.
 
@@
 The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity.
-We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star.
+We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn chemical spot modulation from a rapidly-rotating star.
 This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.
@@
 Our dataset includes a rich variety of classical pulsators.
-We used visual inspection of the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes.
+We visually inspected the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes.
 We identify 23 stars showing $\delta$ Scuti pulsations and 20 with $\gamma$ Doradus pulsations, including 9~with hybrid $\delta$\,Sct/$\gamma$\,Dor variability; 14~slowly pulsating B~stars (SPB stars), 3~$\beta$ Cephei pulsators, 3~Cepheids, as well as 3~O\,stars 5~supergiants showing variability \citep[as in][]{Aerts2018,bowman19}.
-In addition to this, eight stars rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn spot modulation.
+In addition to this, eight stars rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn chemical spot modulation.
 The classes we have determined for each star are listed in Table~\ref{table_all}.

### 2019-07-03 paper/ms.tex
proofread

@@
 These parameters are listed in Table~\ref{rgs}; the stars are noted as showing `RG' variability in Table~\ref{table_all}, whereas this field is left blank for stars of luminosity class III for which oscillations are not unambiguously detected.
-High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models.
-This sample will be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.
+High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars useful as benchmarks for large spectroscopic surveys or testing detailed stellar models.
+This sample will be an addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.
 
@@
 Although the saturation limit is brighter ($T_{mag} \sim 6$) and this problem accordingly affects fewer stars and less badly, there are stars such as $\alpha$~Centauri and $\beta$~Hydri where the bleed column reaches the edge of the chip and a SAP light curve is irrecoverable.
-We expect that TV-min halo photometry will therefore be valuable in ensuring that TESS can observe the very brightest stars.
+We expect that TV-min halo photometry will therefore be important in ensuring that TESS can observe the very brightest stars.
 

### 2019-07-03 paper/ms.tex
conclusions paragraph

@@
 % pretty good sample
+We have presented an updated method for halo photometry, and used this to obtain light curves of 161~stars in \ktwo that were too saturated to be otherwise retrievable.
+These ubiquitously show variability, and we have presented global asteroseismic analysis of 31~red giants and variability classifications for all stars.
+This is a unique legacy sample for \ktwo, dramatically increasing the number of very bright stars that have been characterized with high-precision, rapid-time-cadence space photometry.
+We hope that our data release will be used for a variety of astrophysical investigations.
 

### 2019-07-03 paper/ms.tex
lightkurve in software

@@
 
-\software{\textsc{k2sc} \citep{Aigrain2015,k2sc}; IPython  \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}
+\software{\textsc{k2sc} \citep{Aigrain2015,k2sc}; \texttt{lightkurve} \citep{lightkurve}; IPython \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}
 

### 2019-07-03 paper/ms.tex
software

--- 2019-07-03 paper/ms.tex
@@
 
-\software{\textsc{k2sc} \citep{Aigrain2015,k2sc}; IPython  \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}
+\software{\texttt{halophot} \citep{White2017}; \textsc{k2sc} \citep{Aigrain2015,k2sc}; \texttt{lightkurve} \citep{lightkurve}; \texttt{autograd} \citep{autograd}; \textsc{dbscan} \citep{dbscan}; IPython \citep{PER-GRA:2007}; SciPy \citep{scipy}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}
 

### 2019-07-04 paper/ms.tex
aigrain and g-m comments

@@
 We visually inspected the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes.
-We identify 23 stars showing $\delta$ Scuti pulsations and 20 with $\gamma$ Doradus pulsations, including 9~with hybrid $\delta$\,Sct/$\gamma$\,Dor variability; 14~slowly pulsating B~stars (SPB stars), 3~$\beta$ Cephei pulsators, 3~Cepheids, as well as 3~O\,stars 5~supergiants showing variability \citep[as in][]{Aerts2018,bowman19}.
-In addition to this, eight stars rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn chemical spot modulation.
+We identify 23 stars showing $\delta$ Scuti pulsations and 20 with $\gamma$ Doradus pulsations, including 9~with hybrid $\delta$\,Sct/$\gamma$\,Dor variability; 14~slowly pulsating B~stars (SPB stars), 3~$\beta$ Cephei pulsators, and 3~Cepheids; as well as 3~O\,stars and 5~supergiants showing variability \citep[as in][]{Aerts2018,bowman19}.
+In addition to this, eight stars show rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn chemical spot modulation.
 The classes we have determined for each star are listed in Table~\ref{table_all}.
@@
 This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
+BJSP also acknowledges the financial support of the Clarendon Fund and Balliol College.
 TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118).
+SA acknowledges support from the UK Science and Technology Facilities Council (STFC) under grants ST/N000919/1, ST/S000488/1, and ST/R004846/1.
+
 The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a Director's Discretionary Time program in Campaign 4 as GO4901.

### 2019-07-11 paper/ms.tex
yu affiliation
aerts edits

@@
 \author[0000-0002-0007-6211]{Jie Yu}
-\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
-\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+\affiliation{Max Planck Institute for Solar System Research, Justus-von-Liebig-Weg 3, 37077 G\"{o}ttingen, Germany}
 
@@
 \affiliation{Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, NL-6500 GL Nijmegen, The Netherlands}
+\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"{o}nigstuhl 17, D-69117 Heidelberg}
 
@@
 Applying this to the bright stars across the \ktwo Campaigns reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity.
-We describe our pipeline and present a catalogue of the 161 bright stars, with classifications of their variability, asterosesmic parameters for giants with well-measured solar-like oscillations, and remarks on interesting objects.
+We describe our pipeline and present a catalogue of the 161 bright stars, with classifications of their variability, asteroseismic parameters for red giants with well-measured solar-like oscillations, and remarks on interesting objects.
 These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST).
@@
 While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations.
-Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision light curves.
+Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), to assemble time-series photometry of bright stars, but larger telescopes such as \kepler (0.95\,m) lead to higher-precision light curves.
 
@@
 It was also applied to Aldebaran with further developments by \citet{Farr2018}.
-We follow the `OWL' concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions.
+We follow the Optimized-Weight Linear (OWL) photometry concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions.
 We assume that a star has a wide PSF sampled by many pixels with different sensitivities, which moves around on the detector within a small region and which may vary to a small extent in time.
@@
 The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction for the $x,y$ component evaluated for fixed time represents the pointing systematics.
-We subtracted the systmatics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
+We subtracted the systematics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science.
 Campaigns~9, 10, and~11 were observed in two blocks each, denoted C91/C92, C101/C102 and C111/C112 by the \ktwo Team.
@@
 We found that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP.
-This is unsurprising: that this is one cadence shorter than the 12~cadence thruster firing period.
-In this context we can understand the optimum as suppressing systematics on the same timescale as they occur.
+As this is one cadence shorter than the 12~cadence thruster firing period, we can understand the optimum as suppressing systematics on the same timescale as they occur.
 On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.
@@
 \label{sec:rgs}
-31 of the evolved stars in our sample have detectable stochastically-excited solar-like acoustic (p-mode) oscillations.
+Thirty-one of the red giants in our sample have detectable stochastically-excited solar-like acoustic (p-mode) oscillations.
 In the asymptotic limit, these consist of a comb of modes separated by the large frequency separation \Dnu, approximately the sound-crossing-time of the star, with a Gaussian envelope centred on the frequency of maximum power \numax, which scales with the acoustic cutoff frequency at the star's surface.
@@
 On the other hand, dipole mixed modes, which have a g-mode character in the inner regions of the star, fulfil an asymptotic period spacing determined by the buoyancy frequency inside the star.
-This spacing can be used to accurately determine the stellar evolutionary state and allow to distinguish between hydrogen shell and core helium burning \citep{bedding2011}.
+This spacing can be used to accurately determine the stellar evolutionary stage, and allows us to distinguish between hydrogen shell and core helium burning \citep{bedding2011}.
 Summary plots for a good example of such a star, $\eta$~Cancri, are shown in Figure~\ref{fig:etacnc}.
 
-Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citet{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for the~31 giants for which oscillations are detected with sufficient signal-to-noise.
+Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citet{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for the~31 red giants for which oscillations are detected with sufficient signal-to-noise.
 These parameters are listed in Table~\ref{rgs}; the stars are noted as showing `RG' variability in Table~\ref{table_all}, whereas this field is left blank for stars of luminosity class III for which oscillations are not unambiguously detected.
 High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars useful as benchmarks for large spectroscopic surveys or testing detailed stellar models.
-This sample will be an addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.
+This sample will be an addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic red giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.
 
@@
 We visually inspected the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes.
-We identify 23 stars showing $\delta$ Scuti pulsations and 20 with $\gamma$ Doradus pulsations, including 9~with hybrid $\delta$\,Sct/$\gamma$\,Dor variability; 14~slowly pulsating B~stars (SPB stars), 3~$\beta$ Cephei pulsators, and 3~Cepheids; as well as 3~O\,stars and 5~supergiants showing variability \citep[as in][]{Aerts2018,bowman19}.
-In addition to this, eight stars show rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn chemical spot modulation.
+We identify 23 stars showing $\delta$ Scuti pulsations and 20 with $\gamma$ Doradus pulsations, including 9~with hybrid $\delta$\,Sct/$\gamma$\,Dor variability; 14~slowly pulsating B~stars (SPB stars), 3~$\beta$ Cephei pulsators, and 3~Cepheids; as well as 3~O\,stars and 5~blue supergiants showing low-frequency variability \citep[as in][]{Aerts2018,bowman19}.
+In addition to this, the light curves of eight stars reveal rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn chemical spot modulation.
 The classes we have determined for each star are listed in Table~\ref{table_all}.
@@
 
+The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a Director's Discretionary Time program in Campaign 4 as GO4901.
+We gratefully acknowledge financial support by the National Aeronautics and Space Administration through K2 Guest Observer Programs NNX17AF76G, 80NSSC18K0362, and 80NSSC19K0108, which has been essential in bringing this project to fruition.
+
 This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
@@
 SA acknowledges support from the UK Science and Technology Facilities Council (STFC) under grants ST/N000919/1, ST/S000488/1, and ST/R004846/1.
-
-The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a Director's Discretionary Time program in Campaign 4 as GO4901.
-We gratefully acknowledge financial support by the National Aeronautics and Space Administration through K2 Guest Observer Programs NNX17AF76G, 80NSSC18K0362, and 80NSSC19K0108, which has been essential in bringing this project to fruition.
+CA received funding from the European Research Council (ERC) under the European Union’s Horizon 2020 research and innovation programme (grant agreement N$^\circ$670519: MAMSIE) and from the KU\,Leuven Research Council (grant C16/18/005: PARADISE).
 

### 2019-07-12 paper/ms.tex
hogg edits

@@
 We follow the Optimized-Weight Linear (OWL) photometry concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions.
-We assume that a star has a wide PSF sampled by many pixels with different sensitivities, which moves around on the detector within a small region and which may vary to a small extent in time.
+We assume that a star has a wide PSF sampled by many pixels with different sensitivities.
+This PSF varies at most to a small extent in time.
+The star moves around on the detector within a small region.
 We assume that our time series consists of many epochs sampled with a nearly even cadence.
@@
 Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general.
+In OWL and here, we search for a linear combination of pixels that is invariant with respect to the the noise processes but accurately preserved astrophysical signals.
 
-The additional constraint beyond the OWL axioms is that some pixels are saturated, so that SAP is not possible.
+The additional constraint beyond the OWL axioms is that some pixels are saturated, so that Simple Aperture Photometry (SAP) is inadvisable.
 Instead the measurements are made using the unsaturated pixels $p_j$ at the wings of the broad and structured PSF.
-We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux at epoch $i$ is
+We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux $f_i$ at epoch $i$ is
 
@@
 \begin{equation}
-    Q_{k,l} \equiv {\sum_i{|f_i - f_{i-\delta}|^k}},
+    Q_{k,\delta} \equiv {\sum_i{|f_i - f_{i-\delta}|^k}},
 \end{equation}
 
-\noindent subject to the constraints
+\noindent with an integer lag parameter $\delta$ and an integer $L_k$ norm, subject to the constraints
 
@@
 This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}.
-$Q_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
+$Q_{k,\delta}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
 In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j)$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.
 
-The objective function $Q_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $\delta$.
+The objective function $Q_{k,\delta}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $\delta$.
 For $k = 1$ and $\delta = 1$, $Q_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers \citep[e.g.][]{White2017,Farr2018}, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.

### 2019-07-15 paper/ms.tex
hogg edits
no friends
white affiliations
actually we have c112

@@
 \author[0000-0002-6980-3392]{Timothy R. White}
+\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
 \affiliation{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia}
@@
 
-\author{friends}
 %% Note that the \and command from previous versions of AASTeX is now
@@
 We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or other noise processes.
+
 Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general.
@@
 The additional constraint beyond the OWL axioms is that some pixels are saturated, so that Simple Aperture Photometry (SAP) is inadvisable.
-Instead the measurements are made using the unsaturated pixels $p_j$ at the wings of the broad and structured PSF.
-We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux $f_i$ at epoch $i$ is
+Instead the measurements are made using the unsaturated pixels at the wings of the broad and structured PSF, with counts $p_ij$ where pixels are indexed by $j$ and epoch by $i$.
+We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux $f_i$ at epoch $i$ is a linear
 
@@
 Campaigns~9, 10, and~11 were observed in two blocks each, denoted C91/C92, C101/C102 and C111/C112 by the \ktwo Team.
-The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112.
-As a result \textsc{k2sc}-corrected data are not available for these targets, and no halo light curves at all are available in C112.
+The target pixel files for C91, C92, and C101 include no position information.
+As a result \textsc{k2sc}-corrected data are not available for these targets.
 
@@
 \caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the eclipsing binary 98~Tauri, in a similar format to Figure~\ref{fig:rholeo}.
-The residuals to the position and time GP are not shown, as the time GP fits poorly to the deep eclipse.
+The residuals to the position and time GP are not shown, as the time GP fits poorly to the deep eclipse, though this did not adversely affect the pointing systematics model.
 The polynomial trend and Lomb-Scargle periodograms are conditioned on the out-of-transit points only.}

### 2019-07-15 paper/ms.tex
refer to figures in the text

@@
 
-We calculated halo light curves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data.
+We calculated halo light curves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various values of $\delta \in [1,2500]$ for short cadence data.
 The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}.
@@
 They detected photometric variability at the star's rotation period of 26.8~d and also multiperiodic low-frequency variability ($<1.5 \text{d}^{-1}$).
+The \textsc{k2sc} systematics and variability models, residuals, halo apertures, and periodograms are shown in Figure~\ref{fig:rholeo}, and a comparison with the \citet{Aerts2018} lightcurve in Figure~\ref{rholeo_comparison}.
 There is excellent agreement between the light curves produced by both methods.

### 2019-07-15 paper/ms.tex
69 vir

@@
 Middle two panels: log-flux map (left) and halo log-weight map (right).
-Bottom two panels: periodograms in linear (top) and log (bottom) units of the residuals of the corrected light curve minus the long term polynomial trend.
+Bottom two panels: Lomb-Scargle power spectra in linear (top) and log (bottom) scales of the residuals of the corrected light curve minus the long term polynomial trend.
 Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}.
-The period at maximum power (16\,d) is marked on all plots of this form, though for $\rho$~Leonis all variability is consistent with red noise \citep{Aerts2018,bowman19}.}
+The period at maximum power (16\,d) is marked on all plots of this form; in $\rho$~Leo, variability is attributed to red noise and a 26.8~d rotation period \citep{Aerts2018,bowman19}.}
 \label{fig:rholeo}
@@
 The full sample of stars for which halo apertures were obtained is listed in Table~\ref{table_all}.
-Following the successful pilot observations of the Pleiades B~stars in Campaign~4, we proposed halo photometry through dedicated K2 Guest Observer Programs from Campaign 5 onwards.
+Following the successful pilot observations of the Pleiades B~stars in Campaign~4, we proposed halo photometry through dedicated K2 Guest Observer Programs from Campaign 6 onwards.
 Target selection was performed by cross-matching Hipparcos \citep{leeuwen07} with the K2 Ecliptic Plane Input Catalog \citep[EPIC,][]{huber16} and selecting all targets on silicon brighter than $Kp < 6$ on silicon.
 M~giants which pulsate with periods that are long compared to a K2 campaign were removed.
-We requested short-cadence observations for a small number of unevolved stars for which the expected timescales of solar-like oscillations cannot be sufficiently sampled with long-cadence data.
+We requested short-cadence observations for a small number of unevolved stars for which the expected timescales of oscillations cannot be sufficiently sampled with long-cadence data, such as for $\delta$~Sct stars whose maximum frequencies can exceed the long-cadence Nyquist limit.
 
@@
 % normal apertures in 6
-We include $\alpha$\,Vir (Spica), which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture.
-In Campaign~6 it was assigned a normal aperture due an erroneous estimate of its \kepler magnitude and simple aperture photometry performed extremely poorly, so we have processed these data with the halo pipeline.
+We include $\alpha$\,Vir (Spica) and 69~Vir, which were observed in Campaign~6 without a halo aperture (in Campaign~17 Spica was re-observed, with a halo aperture).
+In Campaign~6 they were assigned normal apertures due an erroneous estimate of their \kepler magnitudes and simple aperture photometry performed extremely poorly, so we have processed these data with the halo pipeline.
 The stars in Campaign~18 in our sample were also on-silicon in Campaign~5, but were not assigned apertures suitable for halo photometry in C5.

### 2019-07-15 paper/ms.tex
beta cep

@@
 \caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the eclipsing binary 98~Tauri, in a similar format to Figure~\ref{fig:rholeo}.
+Blacked-out pixels in the halo weights are background stars which were manually set to zero weight by hand.
 The residuals to the position and time GP are not shown, as the time GP fits poorly to the deep eclipse, though this did not adversely affect the pointing systematics model.
@@
 % do hot star asteroseismology and red giants as benchmarks, interferometry
-Some of the objects presented here are the subject of more detailed work in preparation, namely $\alpha$\,Vir (Spica), interferometry of the Hyades giants, and main-sequence stars with self-driven nonradial modes.
+Some of the objects presented here are the subject of more detailed work in preparation, namely $\alpha$\,Vir (Spica), interferometry and asteroseismology of the Hyades giants, and main-sequence stars with self-driven nonradial modes.
 

### 2019-07-15 paper/ms.tex
lomb-scargle

@@
 Middle two panels: log-flux map (left) and halo log-weight map (right).
-Bottom two panels: Lomb-Scargle power spectra in linear (top) and log (bottom) scales of the residuals of the corrected light curve minus the long term polynomial trend.
+Bottom two panels: Lomb-Scargle power spectra \citep{lomb,scargle} in linear (top) and log (bottom) scales of the residuals of the corrected light curve minus the long term polynomial trend.
 Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}.

### 2019-07-15 paper/ms.tex
metcalfe citations

@@
 Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit.
-Examples treated in the nominal {\it Kepler\/} mission are the prototype classical radial pulsator RR\,Lyr \citep[$V=7.2$;][]{Kolenberg2011}, the solar-like pulsators 16\,Cyg\,AB \citep[$V\approx 6$;][]{2013MNRAS.433.1262W} and $\theta\,$Cyg \citep[$V=4.48$;][]{Guzik2016}, and the massive eclipsing binary V380\,Cyg \citep[$V=5.68$;][]{tkachenko2014}.
+Examples treated in the nominal {\it Kepler\/} mission are the prototype classical radial pulsator RR\,Lyr \citep[$V=7.2$;][]{Kolenberg2011}, the solar-like pulsators 16\,Cyg\,AB \citep[$V\approx 6$;][]{2012ApJ...748L..10M,2013MNRAS.433.1262W,2015ApJ...811L..37M} and $\theta\,$Cyg \citep[$V=4.48$;][]{Guzik2016}, and the massive eclipsing binary V380\,Cyg \citep[$V=5.68$;][]{tkachenko2014}.
 In the nominal \kepler mission SAP was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.

### 2019-07-15 paper/ms.tex
emerging vs future

@@
 We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands.
-We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and to their elders past, present, and future.
+We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and to their elders past, present, and emerging.
 %

### 2019-07-15 scripts/correct_halo.py
figures with no title, and gaussian filter on the periodogram

@@ -53,7 +53,7 @@ def match_cadences(halocads,lccads):
     indices =np.array([1 if j in lccads else 0 for j in halocads])
     return np.where(indices==1)[0]
 
-def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
+def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test',title=True):
     min_p,max_p=1./24.,20.
 
     PW,PH = 8.27, 11.69
@@ -92,7 +92,10 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     plot_pgram(ax_periodogram,frequency,power,spower,formal_name)        
     plot_log_pgram(ax_logpgram,frequency,power,spower,formal_name)  
 
-    fig.suptitle(formal_name,y=0.99,fontsize=20,**font)
+    if title:
+        fig.suptitle(formal_name,y=0.99,fontsize=20,**font)
+    else:
+        print('No title')
     ax_periodogram.set_title('Periodograms')
     ax_fluxmap.set_title('Flux Map')
     ax_weightmap.set_title('TV-Min Weight Map')
@@ -100,9 +103,12 @@ def plot_k2sc(lc,image,weightmap,save_file=None,formal_name='test'):
     if save_file is not None:
         try:
             for fname in save_file:
-                plt.savefig(fname)
+                plt.savefig(fname,bbox_inches='tight')
+                print('Saved to',fname)
         except:
-            plt.savefig(save_file)
+            plt.savefig(save_file,bbox_inches='tight')
+            print('Saved to',fname)
+
 '''-----------------------------------------------------------------
 
 An example call is 
@@ -123,6 +129,7 @@ if __name__ == '__main__':
     ap.add_argument('--just-plot', action = 'store_true', default = False, \
                     help = 'only produce plots')
     ap.add_argument('--epic',default=200000000,type=str,help='EPIC Number')
+    ap.add_argument('--notitle',action='store_true',default=False,help='Title the figures?')
     ap.add_argument('--tpf-fname',default=None,type=str,help='TPF Filename')
     ap.add_argument('--objective', default='tv',type=str,help='Objective function: can be tv, tv_o2, l2v, or l3v')
 
@@ -225,8 +232,13 @@ if __name__ == '__main__':
[…]

### 2019-08-16 paper/ms.tex
colour-magnitude diagram

@@
 Examples treated in the nominal {\it Kepler\/} mission are the prototype classical radial pulsator RR\,Lyr \citep[$V=7.2$;][]{Kolenberg2011}, the solar-like pulsators 16\,Cyg\,AB \citep[$V\approx 6$;][]{2012ApJ...748L..10M,2013MNRAS.433.1262W,2015ApJ...811L..37M} and $\theta\,$Cyg \citep[$V=4.48$;][]{Guzik2016}, and the massive eclipsing binary V380\,Cyg \citep[$V=5.68$;][]{tkachenko2014}.
-In the nominal \kepler mission SAP was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with.
+In the nominal \kepler mission SAP was only attempted for a few bright stars, and in \ktwo, the larger-amplitude spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their instrumental systematics more difficult to deal with.
 While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is not possible for the very brightest stars whose bleed columns may run to the edge of the detector.
@@
 It was also applied to Aldebaran with further developments by \citet{Farr2018}.
+In this Section we will discuss some improvements made to the halo method since those publications, and describe tests of the method using saturated and unsaturated targets.
+
 We follow the Optimized-Weight Linear (OWL) photometry concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions.
@@
 The additional constraint beyond the OWL axioms is that some pixels are saturated, so that Simple Aperture Photometry (SAP) is inadvisable.
-Instead the measurements are made using the unsaturated pixels at the wings of the broad and structured PSF, with counts $p_ij$ where pixels are indexed by $j$ and epoch by $i$.
-We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux $f_i$ at epoch $i$ is a linear
+Instead the measurements are made using the unsaturated pixels at the wings of the broad and structured PSF, with counts $p_{ij}$ where pixels are indexed by $j$ and epoch by $i$.
+We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux $f_i$ at epoch $i$ is
 
@@
 %  improvements
-Unlike other methods for calibrating \kepler systematics, other than the value of $\delta$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
+Unlike other methods for calibrating \kepler systematics, other than the value of~$\delta$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm.
 The signal and the noise are jointly estimated from the data.
-The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
+The method is both self-calibrating, and is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
 
@@
 
-We calculated halo light curves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various values of $\delta \in [1,2500]$ for short cadence data.
+We calculated halo light curves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various values of $\delta \in [1,2500]$ for short-cadence data.
 The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}.
-We found that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP.
+We found that for long-cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP.
 As this is one cadence shorter than the 12~cadence thruster firing period, we can understand the optimum as suppressing systematics on the same timescale as they occur.
-On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.
+On the other hand, for short-cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.
 
-We accordingly use a lag $\delta=10$ for all long cadence light curves, and a lag $\delta=300$ for short cadence for consistency in timescale with the long cadence processing.
+We accordingly use a lag $\delta=10$ for all long-cadence light curves, and a lag $\delta=300$ for short cadence for consistency in timescale with the long-cadence processing.
 
@@
 \plotone{lag_opt_both.pdf}
-\caption{Behaviour of long cadence 6.5~hour CDPP (bottom) and $4 c/d$ systematics power (top) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$.
+\caption{Behaviour of long-cadence 6.5~hour CDPP (bottom) and $4 c/d$ systematics power (top) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$.
 CDPP shows a minimum for L1 norm and $\delta=10$, i.e.
@@
 \begin{figure}
-\plotone{halo_pdc_comparison.png}
+\plotone{halo_pdc_comparison.pdf}
 \caption{Correlation diagram of the \texttt{lightkurve}-computed 6.5\,hr CDPP for \ktwo Campaign~6 stars in the magnitude range $11.5 < Kp < 12.5$, as processed with the PDC pipeline ($x$-axis) and TV-min pipeline ($y$-axis), both after correction and whitening with \textsc{k2sc}.
@@
 The full sample of stars for which halo apertures were obtained is listed in Table~\ref{table_all}.
+A $B$, $V$ color-magnitude diagram is displayed in Figure~\ref{cmd_halo}, omitting the very-red carbon star HR~3541, whose $B-V$ color is 3.23.
 Following the successful pilot observations of the Pleiades B~stars in Campaign~4, we proposed halo photometry through dedicated K2 Guest Observer Programs from Campaign 6 onwards.
@@
 We requested short-cadence observations for a small number of unevolved stars for which the expected timescales of oscillations cannot be sufficiently sampled with long-cadence data, such as for $\delta$~Sct stars whose maximum frequencies can exceed the long-cadence Nyquist limit.
+
+\begin{figure}
+\plotone{cmd_halo.pdf}
+\caption{$B$, $V$ color-magnitude diagram of the halo sample overlaid on a random subset of K2 stars with high-SNR \emph{Gaia} cross-matches, from the \href{https://gaia-kepler.fun}{\nolinkurl{gaia-kepler.fun}} sample, with $B$ and $V$ magnitudes drawn from the EPIC catalog \citep{huber16}.
+We omit the very-red carbon star HR~3541, whose $B-V$ color is 3.23.
+An interactive version of this plot is available as supplementary online material.}
+\label{cmd_halo}
+\end{figure}
 
@@
 For these targets we have provided both long- and short-cadence reductions.
-Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and to $k \in {1,2}$, and for consistency with long cadence, we have adopted a 300~epoch lag (i.e.
+Following the analysis in Section~\ref{method} showing the insensitivity of short-cadence CDPP to lags longer than $\sim 100$\,cad and to $k \in {1,2}$, and for consistency with long cadence, we have adopted a 300~epoch lag (i.e.
 $30 \times$ the long-cadence lag of 10) and the L1 TV objective function.
@@
 
-Analyses for some of our sample have been previously published, we include their light curves in this data release: the Pleiades Seven Sisters \citep{White2017}, $\alpha$~Tau \citep[Aldebaran;][]{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{Arentoft2019}, as well as $\rho$~Leo, which was studied with halo pixels but without our objective functions \citep{Aerts2018}.
+Analyses for some of our sample have been previously published, we include their light curves in this data release: the Pleiades' Seven Sisters \citep{White2017}, $\alpha$~Tau \citep[Aldebaran;][]{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep[Ain;][]{Arentoft2019}, as well as $\rho$~Leo, which was studied with halo pixels but without our objective functions \citep{Aerts2018}.
 
@@
 We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn chemical spot modulation from a rapidly-rotating star.
-This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.
+This star also experiences a V-shaped transit of depth 0.16, which for a 1.87\,\rsun typical A0V star implies an grazing eclipse by a stellar mass companion.
 There are an unusually high number of background stars in the same photometric aperture as 98~Tau, and these were not all detected by \texttt{deathstar} and significantly contaminated the resulting lightcurve.
@@
 Likewise, there may be other convex objective functions, including linear combinations of currently-used objective functions, which offer superior performance, for example by using combinations of different lagged functions to suppress systematics occurring at different timescales.
-The remaining unexplored space of convex objective functions suitable may offer significant improvements on existing self-calibration techniques in high-cadence photometry and related problems in astronomy.
+The remaining unexplored space of convex objective functions may offer significant improvements on existing self-calibration techniques in high-cadence photometry and related problems in astronomy.
 

### 2019-08-16 paper/ms.tex
acknowledge bedell
cmd
referee comments

@@
 We assume that our time series consists of many epochs sampled with a nearly even cadence.
-We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or other noise processes.
+We do not wish to rely on metadata describing the spacecraft motion, pixel gains, PSF variations or other noise processes, at least at this stage.
 
-Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general.
+Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values.
+We choose these weights to be time-invariant but note that this strong constraint is not necessary in general.
+Allowing these weights to vary in time is a possible extension of this method to non-stationary noise processes, but we do not explore this further in this work.
 In OWL and here, we search for a linear combination of pixels that is invariant with respect to the the noise processes but accurately preserved astrophysical signals.
@@
 \begin{equation}
-    Q_{k,\delta} \equiv {\sum_i{|f_i - f_{i-\delta}|^k}},
+    Q_{k,\delta} \equiv {\sum_{i>\delta}{|f_i - f_{i-\delta}|^k}},
 \end{equation}
@@
 $Q_{k,\delta}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
-In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j)$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.
+In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j) = \exp{\tilde{w}_j}/\sum_j(\exp{\tilde{w}_j})$, where $\text{softmax}$ is the normalized exponential function.
+This satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.
+Weight maps displayed in Figures~\ref{fig:rholeo},~\ref{fig:98tau} and~\ref{fig:etacnc} display $w_j$ and not $\tilde{w}_j$.
 
@@
 The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse.
+While $k$ does not have to be an integer in principle, in this implementation we have chosen to restrict our analysis to $k \in \{1,2,3\}$.
 The lag parameter $\delta$ allows for flexibility in modelling systematics occurring at different timescales from epoch-to-epoch, and we investigate its effects below.
@@
 For convenience in the rest of this paper, we will refer to the $k=1$ case as TV, the $k=2$ case as L2V, and the $k=3$ case as L3V.
+As the sampling in K2 is close to uniform but not perfectly uniform, some finite differences actually skip two or three cadences, but these are a small contribution to the final objective function; for very irregularly sampled data, it may be valuable to interpolate onto a uniform grid.
 
@@
 The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}.
-We found that for long-cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP.
-As this is one cadence shorter than the 12~cadence thruster firing period, we can understand the optimum as suppressing systematics on the same timescale as they occur.
+We found that for long-cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP, though not dramatically better than a range of values from $\sim 8-20$.
+As this is around the 12~cadence thruster firing period, we can understand the optimum as suppressing systematics on the same timescale as they occur.
 On the other hand, for short-cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.
@@
 Bottom two panels: Lomb-Scargle power spectra \citep{lomb,scargle} in linear (top) and log (bottom) scales of the residuals of the corrected light curve minus the long term polynomial trend.
-Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}.
+Plots of this form are available on MAST for all long-cadence stars (\dataset[10.17909/t9-6wj4-eb32]{\doi{10.17909/t9-6wj4-eb32}}), together with similar plots for all short-cadence stars but without \textsc{k2sc}.
 The period at maximum power (16\,d) is marked on all plots of this form; in $\rho$~Leo, variability is attributed to red noise and a 26.8~d rotation period \citep{Aerts2018,bowman19}.}
@@
 In this case, by ignoring the pipeline apertures, \texttt{halophot} is in fact generating significantly better light curves.
-Over all stars, we found that the fractional enclosed halo weight in the \kepler pipeline aperture is only $0.19 \pm 0.11$, which suggests that in fact the apertures are systematically smaller than optimal for stars of this magnitude, and that TV-min is using information in the fainter pixels to help correct systematics.
+Over all stars, we found that the fractional enclosed halo weight in the \kepler pipeline aperture is only $0.19 \pm 0.11$, which suggests that in fact the pipeline apertures are systematically smaller than optimal for stars of this magnitude, and that TV-min is using information in the fainter pixels to help correct systematics.
 
@@
 
-The full sample of stars for which halo apertures were obtained is listed in Table~\ref{table_all}.
+The full sample of the 161 stars for which halo apertures were obtained is listed in Table~\ref{table_all}.
 A $B$, $V$ color-magnitude diagram is displayed in Figure~\ref{cmd_halo}, omitting the very-red carbon star HR~3541, whose $B-V$ color is 3.23.
@@
 We omit the very-red carbon star HR~3541, whose $B-V$ color is 3.23.
+The halo sample is seen to be more intrinsically luminous than K2 stars overall, and includes the most intrinsically luminous star observed by K2, $\rho$~Leonis.
 An interactive version of this plot is available as supplementary online material.}
@@
 ][]{Verma2019}.
-On the other hand, dipole mixed modes, which have a g-mode character in the inner regions of the star, fulfil an asymptotic period spacing determined by the buoyancy frequency inside the star.
+On the other hand, dipole mixed modes, which have a g-mode character in the inner regions of the star, fulfill an asymptotic period spacing determined by the buoyancy frequency inside the star.
 This spacing can be used to accurately determine the stellar evolutionary stage, and allows us to distinguish between hydrogen shell and core helium burning \citep{bedding2011}.
@@
 We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn chemical spot modulation from a rapidly-rotating star.
-This star also experiences a V-shaped transit of depth 0.16, which for a 1.87\,\rsun typical A0V star implies an grazing eclipse by a stellar mass companion.
+This star also experiences a V-shaped transit of fractional depth 0.16, which for a 1.87\,\rsun typical A0V star implies a grazing eclipse by a stellar mass companion.
 There are an unusually high number of background stars in the same photometric aperture as 98~Tau, and these were not all detected by \texttt{deathstar} and significantly contaminated the resulting lightcurve.
@@
 
-All light curves presented in this paper are available as High-Level Science Products from the Mikulski Archive for Space Telescopes\footnote{\dataset[10.17909/t9-6wj4-eb32]{\doi{10.17909/t9-6wj4-eb32}}}.
+All light curves presented in this paper are available as High-Level Science Products from the Mikulski Archive for Space Telescopes (MAST)\footnote{\dataset[10.17909/t9-6wj4-eb32]{\doi{10.17909/t9-6wj4-eb32}}}.
 They are also available, together with the source code that produced the survey sample and this manuscript, from \href{https://github.com/benjaminpope/k2halo}{github.com/benjaminpope/k2halo}.
@@
 We acknowledge the support of the Group of Eight universities and the German Academic Exchange Service through the Go8 Australia-Germany Joint Research Co-operation Scheme.
+This work made use of the gaia-kepler.fun crossmatch database created by Megan Bedell.
 
